---
title: 'Nearshore metab. figures '
author: "Kelly Loria"
date: "`r Sys.Date()`"
output:
   html_document:
    theme: simplex
    highlight: tango
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style type="text/css">
body, td {font-size: 13px;}
code.r{font-size: 9px;}
pre {font-size: 11px}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F, message = F)
knitr::opts_knit$set(root.dir = '/Users/kellyloria/Documents/Publications/')
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

```

```{r, echo = F, message = F, include=FALSE}
### Packages
#setwd("/Users/kellyloria/Documents/Publications/2024_stream_metab_output/BWL_k600/")
lapply(c("plyr","dplyr","ggplot2","cowplot",
         "snotelr","dataRetrieval",
         "lubridate","tidyverse", "reshape2", "ggpubr", "ggpattern", "broom.mixed",
         "glmmTMB", "forcats", # order SEM label 
         "lme4", "lmerTest", "MuMIn", "PerformanceAnalytics", "car"), require, character.only=T)
```

## 

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
lapply(c("plyr","dplyr","ggplot2","cowplot",
         "lubridate","tidyverse", "reshape2", "ggpubr", "ggpattern",
         "lme4", "lmerTest", "MuMIn", "PerformanceAnalytics", "car"), require, character.only=T)


site_colors <- c(
  "BWL" = "#3283a8",
  "GBL" = "#a67d17")


shore_colors <- c(
  "BW" = "#3283a8",
  "SS" = "#136F63",
  "GB" = "#a67d17",
  "SH" = "#c76640")

shore_fill <- c(
  "BW" = "#3283a8",
  "SS" = "#136F63",
  "GB" = "#a67d17",
  "SH" = "#c76640")

## Fxn for water year:
water_year <- function(data) {
  # Ensure the `date` column exists
  if (!"date" %in% names(data)) {
    stop("The dataframe must contain a column named 'date'.")
  }
  
  # Convert the `date` column to Date format (if not already)
  data$date <- as.Date(data$date)
  
  # Add the water_year column
  data$water_year <- with(data, {
    year <- as.numeric(format(date, "%Y"))
    month <- as.numeric(format(date, "%m"))
    ifelse(month >= 10, year + 1, year)
  })
  
  return(data)
}

# Define fill patterns for water years
water_year_patterns <- c("wave","weave","stripe","circle", "stripe", "circle")

```

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
dat <-readRDS("/Users/kellyloria/Documents/UNR/MSMmetab/SFS24_Analysis/Final_Scripts/NS_analysis_dat.rds")
```



##### Kernal density plots of GPP and ER

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
 datwy <- water_year(dat)

WY2022_KD_plot <- ggplot(
  datwy %>% 
    dplyr::filter(water_year == 2022, shore %in% c("BW", "GB", "SS")), 
  aes(x = middle_GPP, y = middle_ER, color = shore, shape = shore)
) +
  geom_density_2d(bins = 5, size = 0.25) + 
  geom_point(alpha = 0.5, size=0.75) +
  geom_abline(slope = -1, intercept = 0, color = "black") +  # 1:1 line
  annotate("text", x = 7, y = -1, label = "WY 2022", size = 4, hjust = 0.5, color = "grey50") +
  xlab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression(ER~(mmol~O[2]~m^-3~d^-1))) +
  scale_x_continuous(position = "top", limits = c(0, 13)) +
  scale_y_continuous(limits = c(-18, 0)) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63")
  ) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 1, "GB" = 2, "SS" = 0)
  ) +
  theme_classic()


WY2023_KD_plot <- ggplot(
  datwy %>% 
    dplyr::filter(water_year == 2023, shore %in% c("BW", "GB", "SS")), 
  aes(x = middle_GPP, y = middle_ER, color = shore, shape = shore)
) +
  geom_density_2d(bins = 5, size = 0.25) + 
  geom_point(alpha = 0.5, size=0.75) +
  geom_abline(slope = -1, intercept = 0, color = "black") +  # 1:1 line
  annotate("text", x = 7, y = -1, label = "WY 2023", size = 4, hjust = 0.5, color = "grey50") +
  xlab(NULL) +
  #xlab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression(ER~(mmol~O[2]~m^-3~d^-1))) +
  scale_x_continuous(position = "top", limits = c(0, 13)) +
  scale_y_continuous(limits = c(-18, 0)) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63")
  ) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 1, "GB" = 2, "SS" = 0)
  ) +
  theme_classic()

# 
# BWU_DF_fixed <- covariat_datq%>%dplyr::filter(site=="BWU") %>%
#   filter(water_year < 2024) %>%
#   mutate(water_year = factor(water_year, levels = c(2021, 2022, 2023, 2024))) %>%
#   bind_rows(tibble(GPP_mean = NA, ER_mean = NA, water_year = factor(2024, levels = c(2021, 2022, 2023, 2024))))  # Add dummy row

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

KD_grid <- ggarrange(
  WY2022_KD_plot,
  WY2023_KD_plot,
  labels = c("b"),
  align=c("v"),
  label.x = 0.1,
  label.y = 0.95,
 common.legend = T,
   legend = "bottom",
 heights = c(0.53,0.47),
  hjust = 1,
  vjust = 1,
  ncol = 1, nrow = 2)

KD_grid

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

datwy1 <- datwy %>%dplyr::filter(shore=="SS" | shore=="BW"| shore=="GB")

plot_NEPWY <- ggplot(datwy1%>%dplyr::filter(water_year>2021 & middle_NEP>-25), aes(x = interaction(water_year, shore), y = (middle_NEP), pattern = as.factor(water_year), fill = shore)) +
  geom_jitter(aes(color = shore), width = 0.1, height = 0.01, alpha = 0.25) +  # Adding jittered points with 50% transparency
  geom_boxplot_pattern(alpha = 0.9, outlier.alpha = 0.5,
                       pattern_density = 0.25,  
                       pattern_spacing = 0.05,  
                       pattern_fill = "black",  
                       pattern_angle = 45) +  
  geom_hline(yintercept = 0) +
  scale_pattern_manual(name="WY",
    values = c("2023" = "stripe", "2022" = "none")) +
  scale_fill_manual(name="Shore",
    values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
  scale_color_manual(name="Shore",
    values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
  theme_classic() + #ylim(0,25)+
  theme(legend.position = "right") +
  scale_x_discrete(labels = (c("BW", "BW", "GB", "GB", "SH", "SS", "SS"))) +
  labs(y = expression("NEP"~(mmol~O[2]~m^-3~d^-1)), x = NULL)


```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

KD_grid2 <- ggarrange(
  KD_grid,
  plot_NEPWY,
  labels = c("", "c"),
  align=c("v"),
  label.x = 0.95,
  label.y = 0.98,
# common.legend = T,
  # legend = "bottom",
  hjust = 1,
  vjust = 1,
widths = c(0.75, 0.4),
  ncol = 2, nrow = 1
)

KD_grid2
KD_grid3 <- plot_grid(KD_grid, plot_NEPWY, 
          labels = c("", "c"),
          label_x = 0.8,
          label_y = 0.99,
          align = "v",
          ncol = 2,
          rel_widths = c(1.25, 0.9),
          axis = "tb") # this helps align axes if needed


```




```{r eval=TRUE, echo = TRUE, error=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# identify and scrape data from USGS gages for target sites (BW and GB)

# Define the site numbers for "GB" and "BW"
siteNo_GB <- "10336730"
siteNo_BW <- "10336660"

# Define the parameter codes for flow and stage
pCode_flow <- "00060"
pCode_stage <- "00065"

# Set the start date to "1980-01-01" and end date to today (current date)
start.date <- "2003-09-30"
end.date <- "2024-10-30" #Sys.Date()  # Use the current date as the end date

# Ensure that dplyr functions are correctly used
flow_data_GB <- readNWISdata(siteNumbers = siteNo_GB, parameterCd = pCode_flow, startDate = start.date, endDate = end.date) %>%
  mutate(site = "GBL", catch = "GB") %>%
  dplyr::rename(date = dateTime, dischargeCFS = X_00060_00003) %>%
  mutate(
    dischargeCMS = dischargeCFS * 0.0283168,
    scale_Q = ((dischargeCFS * 0.0283168) / 10.64485)) %>%
    dplyr::select(date, dischargeCFS, site, catch, dischargeCMS, scale_Q)

# View the processed data
print(head(flow_data_GB))

flow_data_BW <- readNWISdata(siteNumbers = siteNo_BW, parameterCd = pCode_flow, startDate = start.date, endDate = end.date) %>%
  mutate(site = "BWL", catch = "BW") %>%
   dplyr::rename(date = dateTime, dischargeCFS = X_00060_00003) %>%
  mutate(
    dischargeCMS = dischargeCFS * 0.0283168,
    scale_Q = ((dischargeCFS * 0.0283168) / 29.00787)
  ) %>%
  dplyr::select(date, dischargeCFS, site, catch, dischargeCMS, scale_Q)


# Combine data for both sites
flow_data <- rbind(flow_data_GB, flow_data_BW)
```


## 2. Hydro-climate characterization

Major question to address:

-   How do the watersheds filter surface water inputs to streams based on differences in local climate (precipitation events, snow-accumulation and snow-melt)?

##### Function for water year:

```{r eval=TRUE, echo = F, error=FALSE, warning=FALSE, message=FALSE}
# fxn for water year
water_year <- function(data) {
  data %>%
    mutate(date = ymd(date)) %>%
    mutate(WaterYear = if_else(month(date) >= 10, year(date) + 1, year(date)))
}
```

##### Read in data from SNOTEL

```{r eval=TRUE, echo = F, include=F, error=FALSE, warning=FALSE, message=FALSE}
# read in the sites data for all SNOTEL sites
target_snow_data <- snotelr::snotel_download(network = "sntl",
                                             site_id = c(848, 615), 
                                             metric = TRUE, internal = TRUE)
target_snow_data$date<- as.Date(target_snow_data$date)

# transform for water year:
target_snow_dat<- water_year(target_snow_data)

#Trim for columns 
target_snow_df <- target_snow_dat %>%
  filter(WaterYear>2003) %>%
  filter(date < as.Date("2024-10-10")) %>%
  mutate(site = case_when(
    site_id == 615 ~ "GBL",
    site_id %in% c(848) ~ "BWL")) %>%
  dplyr::select(site_name,site_id,date,snow_water_equivalent,precipitation_cumulative,
         temperature_max,temperature_min,temperature_mean,precipitation,WaterYear,
         site)
```


## B. Melt and stream flow.

```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}
snowflow_dat <- left_join(target_snow_df, 
                          flow_data, by = c("date", "site")) %>%
  mutate(dischargeCMD = scale_Q * 86400) %>%
  group_by(site, WaterYear)%>%
  arrange(date) %>%  
  mutate(accum_SWE = cumsum(snow_water_equivalent),
         accum_Qm3D = cumsum(dischargeCMD))
  
``` 



### Estimate values for: 

- Total accumulated SWE per water year in mm/yr

- Water yield (cms/km yr)

- Max SWE measurement mm

- Max precipitation accumulation (ppt) in mm 


```{r, echo=T, error=FALSE, warning=FALSE, include=T, message=FALSE}

snowflow_dat_sum <- snowflow_dat%>%
  filter(WaterYear<2025) %>%
  group_by(site, WaterYear) %>%
 dplyr::summarise(Total_SWE = max(accum_SWE, na.rm=T),
            Water_yield = max(accum_Qm3D, na.rm = T),
            Max_SWE = max(snow_water_equivalent, na.rm=T),
            Total_ppt = max(precipitation_cumulative, na.rm=T),
            scale_pk_Q = max(scale_Q, na.rm = T)
            )


### get 20 year water year averages
snowflow_HA <- snowflow_dat_sum%>%
  filter(WaterYear<2025) %>%
  group_by(site) %>%
   dplyr::summarise(mean_SWE_acc = mean(Total_SWE, na.rm=T),
            mean_Water_yield = mean(Water_yield, na.rm = T),
            mean_SWE = mean(Max_SWE, na.rm = T),
            mean_ppt_acc = mean(Total_ppt, na.rm = T)
            )



snowflow_HA1 <- snowflow_dat_sum%>%
  filter(WaterYear>2020 & WaterYear<2024) %>%
  mutate(WY_lab = case_when(
    WaterYear %in% c(2021, 2022) ~ "dry",
    WaterYear %in% c(2023) ~ "wet",
    TRUE ~ NA_character_  )) %>%
    group_by(site,WY_lab) %>%
   dplyr::summarise(mean_SWE_acc = mean(Total_SWE, na.rm=T),
            mean_Water_yield = mean(Water_yield, na.rm = T),
            mean_SWE = mean(Max_SWE, na.rm = T),
            mean_ppt_acc = mean(Total_ppt, na.rm = T),
            m_pk_Q= mean(scale_pk_Q, na.rm=T)
            )

```


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}

ppt_accum_plots <- ggplot(snowflow_dat_sum, aes(x = WaterYear, y = Total_ppt*0.001, color = site, shape=site)) +
  annotate("rect", xmin = -Inf, xmax = 2021.5, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
annotate("rect", xmin = 2023.5, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
  geom_point(size = 1.5, alpha = 0.95, position = position_dodge(width = 0.1)) +
  geom_line(position = position_dodge(width = 0.1))+
    geom_hline(yintercept = 1718.2429*0.001, col = "#3283a8", lty = 2) + 
  geom_hline(yintercept = 843.7667*0.001, col = "#a67d17", lty = 2) + 
  theme_bw() + 
 # geom_vline(xintercept = 2021.5, linetype = "dotted", color = "grey30") +
#    geom_vline(xintercept = 2023.5, linetype = "dotted", color = "grey30") +
  ylab(expression("PPT"~(m~y^-1))) +
  xlab(NULL) + scale_color_manual(values = site_colors) +
  theme(legend.position =  "none") +
        scale_shape_manual(name = "Shore",
                     values = c("BWL" = 19, 
                                "GBL" = 17)) +
        scale_x_continuous(breaks = seq(floor(min(snowflow_dat_sum$WaterYear)), ceiling(max(snowflow_dat_sum$WaterYear)), by = 5), labels = function(x) as.character(round(x)))
  
  
  
```


### streamflow for each catchment WY 22 and WY 23 


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}

snowflow_dat <- as.data.frame(snowflow_dat)

snowflow_dat$date <- as.Date(snowflow_dat$date)



flow_plot1 <- ggplot(
  snowflow_dat %>% filter(date > as.Date("2021-09-30") & date < as.Date("2023-09-14")),
  aes(x = date, y = scale_Q, color = site)
) +
  geom_line(position = position_dodge(width = 0.1)) +
  geom_vline(xintercept = as.Date("2022-09-30"), linetype = "dashed", color = "grey50",ltwd=0.5) +
  theme_classic() + 
  scale_x_date(
  date_breaks = "8 week",
  date_labels = "%b-%y",
  limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))) +
  ylab(expression("Streamflow"~(m^3~s^-1~km^2))) +
  xlab(NULL) + 
   annotate("text", x = as.Date("2022-08-10"), y = 0.03, label = "WY 2022", size = 4, color="grey50")  +
     annotate("text", x = as.Date("2022-11-10"), y = 0.03, label = "WY 2023", size = 4, color="grey50")+

  scale_color_manual(values = site_colors) +
  theme(legend.position = "none")


str(snowflow_dat)
```


### 20 years of SWE accumulation and water yield  

The dashed lines represent the site 20-year average annual (WY) values for total SWE or water catchment normalized water yield 

```{r, warning=F, echo=F,include=F, fig.width=8, fig.height=10}
library(cowplot)

# Create the main plot and the inset
main_plot <- flow_plot1
inset_plot <- ppt_accum_plots

# Combine using draw_plot() with positioning
combined_plot <- ggdraw() +
  draw_plot(main_plot) +  # full-size base plot
  draw_plot(inset_plot, 
            x = 0.075,     # horizontal position (0 = left, 1 = right)
            y = 0.5,     # vertical position (0 = bottom, 1 = top)
            width = 0.45,  # width of the inset (relative to full plot)
            height = 0.45) # height of the inset

# Show it
combined_plot


## align = hv in cow plot high light the years that mountain so that the y axis starts in the same way 
## scale_y_continours

### to scale the water yeild - scale_y_continuous(trans = "log")
```


```{r, warning=F, size = 'small', echo=F, include=F, fig.width=6, fig.height=4}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/Hydro_panel_long.png", plot = combined_plot, width = 8.5, height = 4, units = "in")

```

## Revised Figure 2: 

```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=9, fig.height=6}

fig2_grid <- ggarrange(
  combined_plot,
  KD_grid3,
  labels = c("a", ""),
  align=c("v"),
  label.x = 0.95,
  label.y = 1,
 common.legend = T,
   legend = "bottom",
 heights = c(0.5,0.6),
  hjust = 1,
  vjust = 1,
  ncol = 1, nrow = 2)
fig2_grid


```



```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/Revised_Fig2.png", plot = fig2_grid, width = 8, height = 7.5, units = "in")

```




#### Data structure of SEM: 

Water year **2021:** 2021-06-10 to 2021-09-30

- Just BWNS and GBNS

Water year **2022:** 2021-09-30 to 2022-09-14

- Just BWNS, GBNS, SSNS1

Water year **2023:** 2022-09-30 to 2023-09-14

- Just BWNS, GBNS, and SSNS

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
## BWNS SEM output:
SEM_BW21 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_21.rds") %>%
  mutate(water_year=2021)

SEM_BW22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_22.rds") %>%
  mutate(water_year=2022)

SEM_BW23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_23.rds") %>%
  mutate(water_year=2023)

## GBNS SEM output:
SEM_GB21 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_21.rds") %>%
  mutate(water_year=2021)

SEM_GB22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_22.rds") %>%
  mutate(water_year=2022)

SEM_GB23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_23.rds") %>%
  mutate(water_year=2023)


## SSNS SEM output:
SEM_SS22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_22.rds") %>%
  mutate(water_year=2022)

SEM_SS23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_23.rds") %>%
  mutate(water_year=2023)

```



```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
# 
# SEM_df_GPP_22 <- rbind(SEM_BW22, SEM_GB22, SEM_SS22)
# 
# ci_summary_overall <- SEM_df_GPP_22 %>%
#   dplyr::group_by(Coefficient, shore, water_year) %>%
#   dplyr:: summarize(
#     mean = mean(Estimate),
#     l_95 = quantile(Estimate, 0.025),
#     u_95 = quantile(Estimate, 0.975),
#     .groups = "drop"
#   )
# 
# 
# coef_order <- c(
#   "b_plotGPP_plot_GPP_lag",
#   "b_plotGPP_lake_tempC",
#   "b_plotGPP_light_mean",
#   "b_plotGPP_flow_mean",
#   "b_laketempC_flow_mean",
#   "b_laketempC_ppt_mm",
#   "b_lightmean_flow_mean",
#   "b_lightmean_ppt_mm"
# )
# 
# ci_summary_overall1 <- ci_summary_overall %>%
#   mutate(Coefficient = fct_relevel(Coefficient, rev(coef_order)))
# 
# 
# # coefficient plot
# coef_plot_gpp_22 <- ggplot(ci_summary_overall1, aes(x = mean, y = Coefficient, color = shore, shape=shore)) +
#   geom_point(position = position_dodge(width = 0.6), size = 2.5) +
#   geom_errorbarh(aes(xmin = l_95, xmax = u_95),
#                  position = position_dodge(width = 0.6), height = 0) +
#   geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
#   scale_color_manual(name = "Shore", values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
#   theme_minimal() +
#   xlim(-5.25, 1.40) +
#   labs(
#     x = NULL,
#     y = "Water year 2022",
#     title = "GPP",
#   ) +
#   theme(
#     axis.text.y = element_text(size = 10),
#     legend.position = "right"
#   )  + scale_y_discrete(labels = c(
#     "b_plotGPP_plot_GPP_lag" = "Metab. ~ AR",
#     "b_plotGPP_lake_tempC" = "Metab. ~ Temp.",
#     "b_plotGPP_light_mean" = "Metab. ~ Light",
#     "b_plotGPP_flow_mean" = "Metab. ~ Flow",
#     "b_laketempC_flow_mean" = "Temp ~ Flow",
#     "b_laketempC_ppt_mm" = "Temp ~ PPT",
#     "b_lightmean_flow_mean" = "Light ~ Flow",
#     "b_lightmean_ppt_mm" = "Light ~ PPT"
#   ))
# 
# coef_plot_gpp_22

```


```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
# 
# SEM_df_GPP_23 <- rbind(SEM_BW23, SEM_GB23, SEM_SS23)
# 
# ci_summary_overall <- SEM_df_GPP_23 %>%
#   dplyr::group_by(Coefficient, shore, water_year) %>%
#   dplyr:: summarize(
#     mean = mean(Estimate),
#     l_95 = quantile(Estimate, 0.025),
#     u_95 = quantile(Estimate, 0.975),
#     .groups = "drop"
#   )
# 
# 
# coef_order <- c(
#   "b_plotGPP_plot_GPP_lag",
#   "b_plotGPP_lake_tempC",
#   "b_plotGPP_light_mean",
#   "b_plotGPP_flow_mean",
#   "b_laketempC_flow_mean",
#   "b_laketempC_ppt_mm",
#   "b_lightmean_flow_mean",
#   "b_lightmean_ppt_mm"
# )
# 
# ci_summary_overall1 <- ci_summary_overall %>%
#   mutate(Coefficient = fct_relevel(Coefficient, rev(coef_order)))
# 
# 
# # coefficient plot
# coef_plot_gpp_23 <- ggplot(ci_summary_overall1, aes(x = mean, y = Coefficient, color = shore, shape=shore)) +
#   geom_point(position = position_dodge(width = 0.6), size = 2.5) +
#   geom_errorbarh(aes(xmin = l_95, xmax = u_95),
#                  position = position_dodge(width = 0.6), height = 0) +
#   geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
#   scale_color_manual(name = "Shore", values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
#   theme_minimal() +
#   xlim(-5.25, 1.40) +
#   labs(
#     x = "Estimate (posterior mean ± 95% CI)",
#     y = "Water year 2023",
#   ) +
#   theme(
#     axis.text.y = element_text(size = 10),
#     legend.position = "right"
#   )  + scale_y_discrete(labels = c(
#     "b_plotGPP_plot_GPP_lag" = "Metab. ~ AR",
#     "b_plotGPP_lake_tempC" = "Metab. ~ Temp.",
#     "b_plotGPP_light_mean" = "Metab. ~ Light",
#     "b_plotGPP_flow_mean" = "Metab. ~ Flow",
#     "b_laketempC_flow_mean" = "Temp ~ Flow",
#     "b_laketempC_ppt_mm" = "Temp ~ PPT",
#     "b_lightmean_flow_mean" = "Light ~ Flow",
#     "b_lightmean_ppt_mm" = "Light ~ PPT"
#   ))
# 
# coef_plot_gpp_23

```

```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=8, fig.height=6}

# SEM_GPP_grid <- ggarrange(
#   coef_plot_gpp_22,
#   coef_plot_gpp_23,
#  # labels = c("a", "b"),
#   align=c("v"),
#   #label.x = 0.1, 
#   #label.y = 1, 
#  common.legend = T,
#    legend = "bottom",
#   hjust = 1,  
#   vjust = 1,  
#   ncol = 1, nrow = 2) 
# 
# SEM_GPP_grid

```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=8, fig.height=6}

SEM_df_GPP_comb <- rbind(SEM_BW22, SEM_GB22, SEM_SS22, 
                         SEM_BW23, SEM_GB23, SEM_SS23)

ci_summary_overall <- SEM_df_GPP_comb %>%
  dplyr::group_by(Coefficient, shore, water_year) %>%
  dplyr:: summarize(
    mean = mean(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )


coef_order <- c(
  "b_plotGPP_plot_GPP_lag",
  "b_plotGPP_lake_tempC",
  "b_plotGPP_light_mean",
  "b_plotGPP_flow_mean",
  "b_laketempC_flow_mean",
  "b_laketempC_ppt_mm",
  "b_lightmean_flow_mean",
  "b_lightmean_ppt_mm"
)

ci_summary_overall1 <- ci_summary_overall %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_order)))

levels(ci_summary_overall1$Coefficient)


ci_summary_overall1 <- ci_summary_overall1 %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "BW 2022",
    shore == "BW" & water_year == 2023 ~ "BW 2023",
    shore == "GB" & water_year == 2022 ~ "GB 2022",
    shore == "GB" & water_year == 2023 ~ "GB 2023",
    shore == "SS" & water_year == 2022 ~ "SS 2022",
    shore == "SS" & water_year == 2023 ~ "SS 2023",
    TRUE ~ "Other"
  ))

####
coef_plot_gpp <- ggplot(ci_summary_overall1, aes(x = mean, y = Coefficient, 
                                                 color = point_shape, shape = point_shape)) +
  geom_point(position = position_dodge(width = 0.5), size = 3, alpha=0.9) +
  geom_errorbarh(aes(xmin = l_95, xmax = u_95),
                 position = position_dodge(width = 0.5), height = 0, alpha=0.45) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
  scale_color_manual(name = "Shore and water year", 
                     values = c("BW 2022" = "#3283a8", "BW 2023" = "#3283a8",
                                "GB 2022" = "#a67d17", "GB 2023" = "#a67d17",
                                "SS 2022" = "#136F63", "SS 2023" = "#136F63")) +
  
  scale_shape_manual(name = "Shore and water year",
                     values = c("BW 2022" = 1, "BW 2023" = 19, 
                                "GB 2022" = 2, "GB 2023" = 17, 
                                "SS 2022" = 0, "SS 2023" = 15)) +

  theme_minimal() +
  labs(
    x = "Estimate (posterior mean ± 95% CI)",
    y = NULL,
    title = "GPP"
  ) +
  theme(
    axis.text.y = element_text(size = 10),
    legend.position = "right"
  ) +
  scale_y_discrete(labels = c(
    "b_plotGPP_plot_GPP_lag" = "Metab. ~ AR",
    "b_plotGPP_lake_tempC" = "Metab. ~ Temp.",
    "b_plotGPP_light_mean" = "Metab. ~ Light",
    "b_plotGPP_flow_mean" = "Metab. ~ Flow",
    "b_laketempC_flow_mean" = "Temp ~ Flow",
    "b_laketempC_ppt_mm" = "Temp ~ PPT",
    "b_lightmean_flow_mean" = "Light ~ Flow",
    "b_lightmean_ppt_mm" = "Light ~ PPT"
  ))


coef_plot_gpp

```

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
## BWNS SEM output:
SEM_BW21e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_BW_21.rds") %>%
  mutate(water_year=2021)

SEM_BW22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_BW_22.rds") %>%
  mutate(water_year=2022)

SEM_BW23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_BW_23.rds") %>%
  mutate(water_year=2023)

## GBNS SEM output:
SEM_GB21e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_GB_21.rds") %>%
  mutate(water_year=2021)

SEM_GB22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_GB_22.rds") %>%
  mutate(water_year=2022)

SEM_GB23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_GB_23.rds") %>%
  mutate(water_year=2023)


## SSNS SEM output:
SEM_SS22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_SS_22.rds") %>%
  mutate(water_year=2022)

SEM_SS23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/ER_posterior_samples_melted_SS_23.rds") %>%
  mutate(water_year=2023)

```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=8, fig.height=6}

SEM_df_ER_comb <- rbind(SEM_BW22e, SEM_GB22e, SEM_SS22e, 
                         SEM_BW23e, SEM_GB23e, SEM_SS23e)

ci_summary_overalle <- SEM_df_ER_comb %>%
  dplyr::group_by(Coefficient, shore, water_year) %>%
  dplyr:: summarize(
    mean = mean(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )


coef_ordere <- c(
  "b_plotER_plot_ER_lag",
  "b_plotER_lake_tempC",
  "b_plotER_light_mean",
  "b_plotER_flow_mean",
  "b_laketempC_flow_mean",
  "b_laketempC_ppt_mm",
  "b_lightmean_flow_mean",
  "b_lightmean_ppt_mm"
)

ci_summary_overall1e<- ci_summary_overalle %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_ordere)))

levels(ci_summary_overall1$Coefficient)


ci_summary_overall1e <- ci_summary_overall1e %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "BW 2022",
    shore == "BW" & water_year == 2023 ~ "BW 2023",
    shore == "GB" & water_year == 2022 ~ "GB 2022",
    shore == "GB" & water_year == 2023 ~ "GB 2023",
    shore == "SS" & water_year == 2022 ~ "SS 2022",
    shore == "SS" & water_year == 2023 ~ "SS 2023",
    TRUE ~ "Other"
  ))

####
coef_plot_er <- ggplot(ci_summary_overall1e, aes(x = mean, y = Coefficient, 
                                                 color = point_shape, shape = point_shape)) +
  geom_point(position = position_dodge(width = 0.5), size = 3, alpha=0.9) +
  geom_errorbarh(aes(xmin = l_95, xmax = u_95),
                 position = position_dodge(width = 0.5), height = 0, alpha=0.45) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
  scale_color_manual(name = "Shore and water year", 
                     values = c("BW 2022" = "#3283a8", "BW 2023" = "#3283a8",
                                "GB 2022" = "#a67d17", "GB 2023" = "#a67d17",
                                "SS 2022" = "#136F63", "SS 2023" = "#136F63")) +
  
  scale_shape_manual(name = "Shore and water year",
                     values = c("BW 2022" = 1, "BW 2023" = 19, 
                                "GB 2022" = 2, "GB 2023" = 17, 
                                "SS 2022" = 0, "SS 2023" = 15)) +

  theme_minimal() +
  labs(
    x = "Estimate (posterior mean ± 95% CI)",
    y = NULL,
    title = "ER"
  ) +
  theme(
    axis.text.y = element_text(size = 10),
    legend.position = "right"
  ) + scale_y_discrete(labels=NULL)
# +
#   scale_y_discrete(labels = c(
#     "b_plotER_plot_ER_lag" = "Metab. ~ AR",
#     "b_plotER_lake_tempC" = "Metab. ~ Temp.",
#     "b_plotER_light_mean" = "Metab. ~ Light",
#     "b_plotER_flow_mean" = "Metab. ~ Flow",
#     "b_laketempC_flow_mean" = "Temp ~ Flow",
#     "b_laketempC_ppt_mm" = "Temp ~ PPT",
#     "b_lightmean_flow_mean" = "Light ~ Flow",
#     "b_lightmean_ppt_mm" = "Light ~ PPT"
#   ))


coef_plot_er

```



```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=8, fig.height=6}

SEM_grid <- ggarrange(
  coef_plot_gpp,
  coef_plot_er,
 # labels = c("a", "b"),
  align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
 common.legend = T,
   legend = "bottom",
  hjust = 0.1,
  vjust = 1,
  ncol = 2, nrow = 1)

SEM_grid

```




```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
# 
# library(ggridges)
# library(ggplot2)
# library(dplyr)
# 
# # Optional: Filter out coefficients you don't want
# SEM_df_GPP_22_filtered <- SEM_df_GPP_22 %>%
#   filter(!(shore == "SS" & Coefficient %in% c("b_plotGPP_flow_mean", "b_laketempC_flow_mean", "b_lightmean_flow_mean")))
# 
# # Plot using ggridges
# coef_density_plot <- ggplot(SEM_df_GPP_22_filtered, 
#                             aes(x = Estimate, y = Coefficient, fill = shore, color = shore)) +
#   ggridges::geom_density_ridges(
#     scale = 1.5, 
#     alpha = 0.6,
#     rel_min_height = 0.05,
#     color = "black"
#   ) +
#   geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
#   scale_fill_manual(values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
#   scale_color_manual(values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
#   theme_minimal() +
#   labs(
#     x = "Mean posterior estimate and 95% CI",
#     y = "Water year 2023",
#   ) +
#   theme(
#     axis.text.y = element_text(size = 10),
#     legend.position = "right"
#   )
# 
# coef_density_plot


```

