---
title: 'Nearshore metab. figures '
author: "Kelly Loria"
date: "`r Sys.Date()`"
output:
   html_document:
    theme: simplex
    highlight: tango
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style type="text/css">
body, td {font-size: 13px;}
code.r{font-size: 9px;}
pre {font-size: 11px}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F, message = F)
knitr::opts_knit$set(root.dir = '/Users/kellyloria/Documents/Publications/')
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

```

```{r, echo = F, message = F, include=FALSE}
### Packages
#setwd("/Users/kellyloria/Documents/Publications/2024_stream_metab_output/BWL_k600/")
lapply(c("plyr","dplyr","ggplot2","cowplot",
         "snotelr","dataRetrieval",
         "lubridate","tidyverse", "reshape2", "ggpubr", "ggpattern", "broom.mixed",
         "glmmTMB", "forcats", # order SEM label 
         "lme4", "lmerTest", "MuMIn", "PerformanceAnalytics", "car"), require, character.only=T)
```

### Question 1
How does stream inflow regulate littoral environmental conditions (e.g. nutrient availability, water temperature, and light availability) and nearshore metabolism between a relatively dry water year versus wet water year?

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
lapply(c("plyr","dplyr","ggplot2","cowplot",
         "lubridate","tidyverse", "reshape2", "ggpubr", "ggpattern",
         "lme4", "lmerTest", "MuMIn", "PerformanceAnalytics", "car"), require, character.only=T)


site_colors <- c(
  "BWL" = "#3283a8",
  "GBL" = "#a67d17")


shore_colors <- c(
  "BW" = "#3283a8",
  "SS" = "#136F63",
  "GB" = "#a67d17",
  "SH" = "#c76640")

shore_fill <- c(
  "BW" = "#3283a8",
  "SS" = "#136F63",
  "GB" = "#a67d17",
  "SH" = "#c76640")

## Fxn for water year:
water_year <- function(data) {
  # Ensure the `date` column exists
  if (!"date" %in% names(data)) {
    stop("The dataframe must contain a column named 'date'.")
  }
  
  # Convert the `date` column to Date format (if not already)
  data$date <- as.Date(data$date)
  
  # Add the water_year column
  data$water_year <- with(data, {
    year <- as.numeric(format(date, "%Y"))
    month <- as.numeric(format(date, "%m"))
    ifelse(month >= 10, year + 1, year)
  })
  
  return(data)
}

# Define fill patterns for water years
water_year_patterns <- c("wave","weave","stripe","circle", "stripe", "circle")

```

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
dat <-readRDS("/Users/kellyloria/Documents/UNR/MSMmetab/SFS24_Analysis/Final_Scripts/NS_analysis_dat.rds")
```



##### Kernal density plots of GPP and ER

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}
 datwy <- water_year(dat)

WY2022_KD_plot <- ggplot(
  datwy %>% 
    dplyr::filter(WaterYear == 2022, shore %in% c("BW", "GB", "SS")), 
  aes(x = middle_GPP, y = middle_ER, color = shore, shape = shore)
) +
  geom_density_2d(bins = 5, size = 0.45) + 
  geom_point(alpha = 0.5, size=0.75) +
  geom_abline(slope = -1, intercept = 0, color = "black") +  # 1:1 line
  annotate("text", x = 20, y = -1, label = "WY 2022", size = 4, hjust = 0.5, color = "grey50") +
  xlab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression(ER~(mmol~O[2]~m^-3~d^-1))) +
  scale_x_continuous(position = "top", limits = c(0, 25)) +
  scale_y_continuous(limits = c(-25, 0)) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63")
  ) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 1, "GB" = 2, "SS" = 0)
  ) + theme(legend.position = "none") +
  guides(color = "none", shape = "none") +
  theme_classic()


WY2023_KD_plot <- ggplot(
  datwy %>% 
    dplyr::filter(WaterYear == 2023, shore %in% c("BW", "GB", "SS")), 
  aes(x = middle_GPP, y = middle_ER, color = shore, shape = shore)
) +
  geom_density_2d(bins = 5, size = 0.45) + 
  geom_point(alpha = 0.5, size=0.75) +
  geom_abline(slope = -1, intercept = 0, color = "black") +  # 1:1 line
  annotate("text", x = 20, y = -1, label = "WY 2023", size = 4, hjust = 0.5, color = "grey50") +
  xlab(NULL) +
  #xlab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression(ER~(mmol~O[2]~m^-3~d^-1))) +
  scale_x_continuous(position = "top", limits = c(0, 25)) +
  scale_y_continuous(limits = c(-25, 0)) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63")
  ) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 1, "GB" = 2, "SS" = 0)
  ) + theme(legend.position = "none") +
  guides(color = "none", shape = "none") +
  theme_classic()

# 
# BWU_DF_fixed <- covariat_datq%>%dplyr::filter(site=="BWU") %>%
#   filter(water_year < 2024) %>%
#   mutate(water_year = factor(water_year, levels = c(2021, 2022, 2023, 2024))) %>%
#   bind_rows(tibble(GPP_mean = NA, ER_mean = NA, water_year = factor(2024, levels = c(2021, 2022, 2023, 2024))))  # Add dummy row

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

KD_grid <- ggarrange(
  WY2022_KD_plot,
  WY2023_KD_plot,
  labels = c("b"),
  align=c("v"),
  label.x = 0.1,
  label.y = 0.95,
# common.legend = T,
   #legend = "right",
 heights = c(0.53,0.47),
#  hjust = 1,
#  vjust = 1,
  ncol = 1, nrow = 2)

KD_grid

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

datwy1 <- datwy %>%dplyr::filter(shore=="SS" | shore=="BW"| shore=="GB")

plot_NEPWY <- ggplot(datwy1%>%dplyr::filter(WaterYear>2021 & middle_NEP>-25), aes(x = interaction(WaterYear, shore), y = (middle_NEP), pattern = as.factor(WaterYear), fill = shore)) +
  geom_jitter(aes(color = shore), width = 0.1, height = 0.01, alpha = 0.25) +  # Adding jittered points with 50% transparency
  geom_boxplot_pattern(alpha = 0.9, outlier.alpha = 0.5,
                       pattern_density = 0.25,  
                       pattern_spacing = 0.05,  
                       pattern_fill = "black",  
                       pattern_angle = 45) +  
  geom_hline(yintercept = 0) +
  scale_pattern_manual(name="WY",
    values = c("2023" = "stripe", "2022" = "none"),   labels = c(
    "2023" = "Wet",
    "2022" = "Dry")) +
  scale_fill_manual(
  name = "Shore",
  values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640"),
  labels = c(
    SS = "No inflow",
    BW = "Large inflow",
    GB = "Small inflow"
  )
) +
scale_color_manual(
  name = "Shore",
  values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640"),
  labels = c(
    SS = "No inflow",
    BW = "Large inflow",
    GB = "Small inflow"
  )
) +
  theme_classic() + #ylim(0,25)+
  theme(legend.position = "right") +
  guides(
    fill = guide_legend(nrow = 4),
    color = guide_legend(nrow = 5)) +
  scale_x_discrete(labels = (c("BW", "BW", "GB", "GB", "SH", "SS", "SS"))) +
  labs(y = expression("NEP"~(mmol~O[2]~m^-3~d^-1)), x = NULL)


```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=6}

KD_grid2 <- ggarrange(
  KD_grid,
  plot_NEPWY,
  labels = c("", "c"),
  align=c("v"),
  label.x = 0.95,
  label.y = 0.98,
# common.legend = T,
  # legend = "bottom",
#  hjust = 1,
  vjust = 1,
widths = c(0.75, 0.4),
  ncol = 2, nrow = 1
)

KD_grid2
# KD_grid3 <- plot_grid(KD_grid, plot_NEPWY, 
#           labels = c("", "c"),
#           label_x = 0.8,
#           label_y = 0.99,
#           align = "h",
#           ncol = 2,
#           #rel_widths = c(1.15, 1),
#           rel_heights = c(2, 0.1),
#           axis = "tb") # this helps align axes if needed
# 

KD_grid3 <- plot_grid(
  KD_grid, plot_NEPWY, 
  labels = c("", "c"),
  label_x = 0.8,
  label_y = 0.99,
  align = "h",
  ncol = 2,
  rel_widths = c(1, 1.15),  # Adjust these to your taste
  axis = "tb"
)



```


```{r, eval=T, echo = F, error=FALSE, warning=FALSE, message=FALSE, include=FALSE}

flow_df <- readRDS("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/data/CH1_flow_df.rds")
flow_df
```


```{r, eval=TRUE, echo = F, error=FALSE, warning=FALSE, message=FALSE}
##### Function for water year:
# fxn for water year
water_year <- function(data) {
  data %>%
    mutate(date = ymd(date)) %>%
    mutate(WaterYear = if_else(month(date) >= 10, year(date) + 1, year(date)))
}
```


```{r, eval=TRUE, echo = F, include=F, error=FALSE, warning=FALSE, message=FALSE}
##### Read in data from SNOTEL

# read in the sites data for all SNOTEL sites
target_snow_data <- snotelr::snotel_download(network = "sntl",
                                             site_id = c(848, 615), 
                                             metric = TRUE, internal = TRUE)
target_snow_data$date<- as.Date(target_snow_data$date)

# transform for water year:
target_snow_dat<- water_year(target_snow_data)

#Trim for columns 
target_snow_df <- target_snow_dat %>%
  filter(WaterYear>2003) %>%
  filter(date < as.Date("2024-10-10")) %>%
  mutate(site = case_when(
    site_id == 615 ~ "GBL",
    site_id %in% c(848) ~ "BWL")) %>%
  dplyr::select(site_name,site_id,date,snow_water_equivalent,precipitation_cumulative,
         temperature_max,temperature_min,temperature_mean,precipitation,WaterYear,
         site)
```


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}
## B. Melt and stream flow.

snowflow_dat <- target_snow_df %>%
  dplyr::left_join(flow_df, by = c("date", "site")) %>%
  mutate(dischargeCMD = Q_m * 86400) %>%
  dplyr::group_by(site, WaterYear)%>%
  arrange(date) %>%  
  mutate(accum_SWE = cumsum(snow_water_equivalent),
         accum_Qm3D = cumsum(dischargeCMD))
  
``` 



```{r, echo=T, error=FALSE, warning=FALSE, include=F, message=FALSE}

snowflow_dat_sum <- snowflow_dat%>%
  filter(WaterYear<2025) %>%
 dplyr:: group_by(site, WaterYear) %>%
 dplyr::summarise(
            Water_yield = max(accum_Qm3D, na.rm = T),
            Total_ppt = max(precipitation_cumulative, na.rm=T)
            )

```


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}

ppt_accum_plots <- ggplot(snowflow_dat_sum, aes(x = WaterYear, y = Total_ppt*0.001, color = site, shape=site)) +
  annotate("rect", xmin = -Inf, xmax = 2021.5, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
annotate("rect", xmin = 2023.5, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
  geom_point(size = 1.5, alpha = 0.95, position = position_dodge(width = 0.1)) +
  geom_line(position = position_dodge(width = 0.1))+
    geom_hline(yintercept = 1718.2429*0.001, col = "#3283a8", lty = 2) + 
  geom_hline(yintercept = 843.7667*0.001, col = "#a67d17", lty = 2) + 
  theme_bw() + 
 # geom_vline(xintercept = 2021.5, linetype = "dotted", color = "grey30") +
#    geom_vline(xintercept = 2023.5, linetype = "dotted", color = "grey30") +
  ylab(expression("PPT"~(m~y^-1))) +
  xlab(NULL) + scale_color_manual(values = site_colors) +
  theme(legend.position =  "none") +
        scale_shape_manual(name = "Shore",
                     values = c("BWL" = 19, 
                                "GBL" = 17)) +
        scale_x_continuous(breaks = seq(floor(min(snowflow_dat_sum$WaterYear)), ceiling(max(snowflow_dat_sum$WaterYear)), by = 5), labels = function(x) as.character(round(x)))
  
  
  
```



```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}
### streamflow for each catchment WY 22 and WY 23 


snowflow_dat <- as.data.frame(snowflow_dat)

snowflow_dat$date <- as.Date(snowflow_dat$date)



flow_plot1 <- ggplot(
  snowflow_dat %>% filter(date > as.Date("2021-09-30") & date < as.Date("2023-09-14")),
  aes(x = date, y = Q_m, color = site)
) +
  geom_line(position = position_dodge(width = 0.1)) +
  geom_vline(xintercept = as.Date("2022-09-30"), linetype = "dashed", color = "grey50",ltwd=0.5) +
  theme_classic() + 
  scale_x_date(
  date_breaks = "8 week",
  date_labels = "%b-%y",
  limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))) +
  ylab(expression("Streamflow"~(m^3~s^-1~km^2))) +
  xlab(NULL) + 
   annotate("text", x = as.Date("2022-08-10"), y = 0.65, label = "WY 2022", size = 3.5, color="grey50")  +
     annotate("text", x = as.Date("2022-11-15"), y = 0.65, label = "WY 2023", size = 3.5, color="grey50")+

  scale_color_manual(values = site_colors) +
    theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```


20 years of SWE accumulation and water yield  

The dashed lines represent the site 20-year average annual (WY) values for total SWE or water catchment normalized water yield 

```{r, warning=F, echo=F,include=F, fig.width=8, fig.height=10}
library(cowplot)

# Create the main plot and the inset
main_plot <- flow_plot1
inset_plot <- ppt_accum_plots

# Combine using draw_plot() with positioning
combined_plot <- ggdraw() +
  draw_plot(main_plot) +  # full-size base plot
  draw_plot(inset_plot, 
            x = 0.095,     # horizontal position (0 = left, 1 = right)
            y = 0.5,     # vertical position (0 = bottom, 1 = top)
            width = 0.42,  # width of the inset (relative to full plot)
            height = 0.45) # height of the inset

# Show it
combined_plot


## align = hv in cow plot high light the years that mountain so that the y axis starts in the same way 
## scale_y_continours

### to scale the water yeild - scale_y_continuous(trans = "log")
```


```{r, warning=F, size = 'small', echo=F, include=F, fig.width=6, fig.height=4}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/Hydro_panel_long.png", plot = combined_plot, width = 8.5, height = 4, units = "in")

```

## Revised Figure 2: 

```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=9, fig.height=10}

fig2_grid <- ggarrange(
  combined_plot,
  KD_grid3,
  labels = c("a", ""),
 align=c("v"),
  label.x = 0.95,
  label.y = 1,
 common.legend = T,
   legend = "bottom",
 heights = c(0.35,0.65),
 # hjust = 1,
  #vjust = 1,
  ncol = 1, nrow = 2)
fig2_grid


```



```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Revised_Fig2.png", plot = fig2_grid, width = 6.35, height = 7.5, units = "in")

```




#### Data structure of SEM: 

Water year **2021:** 2021-06-10 to 2021-09-30

- Just BWNS and GBNS

Water year **2022:** 2021-09-30 to 2022-09-14

- Just BWNS, GBNS, SSNS1

Water year **2023:** 2022-09-30 to 2023-09-14

- Just BWNS, GBNS, and SSNS

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}

SEM_BW22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_22_final_logflow.rds") %>%
  mutate(water_year=2022)

SEM_BW23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_23_final_logflow.rds") %>%
  mutate(water_year=2023)


SEM_GB22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_22_GPP_logflow.rds") %>%
  mutate(water_year=2022)

SEM_GB23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_23_GPP_logflow.rds") %>%
  mutate(water_year=2023)


## SSNS SEM output:
SEM_SS22 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_22_finalv2.rds") %>%
  mutate(water_year=2022)

SEM_SS23 <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_23_finalv2.rds") %>%
  mutate(water_year=2023)

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=5}

SEM_df_GPP_comb <- rbind(SEM_BW22, SEM_GB22, SEM_SS22, 
                         SEM_BW23, SEM_GB23, SEM_SS23)

ci_summary_overall <- SEM_df_GPP_comb %>%
  dplyr::group_by(Coefficient, shore, water_year) %>%
  dplyr:: summarize(
    median = median(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )

# write_csv(ci_summary_overall, "/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/SEM_summary/SEM_CI_GPP_logflow.csv")


ci_summary_overallT <- SEM_df_GPP_comb %>%
  dplyr::group_by(Coefficient, water_year) %>%
  dplyr:: summarize(
    median = median(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )


coef_order <- c(
  "b_plotGPP_plot_GPP_lag",
  "b_plotGPP_lake_tempC",
  "b_plotGPP_light_mean",
  "b_plotGPP_flow_mean",
  "b_laketempC_flow_mean",
  "b_laketempC_ppt_mm",
  "b_lightmean_flow_mean",
  "b_lightmean_ppt_mm",
  "b_flowmean_ppt_mm"
)

ci_summary_overall1 <- ci_summary_overall %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_order)))

levels(ci_summary_overall1$Coefficient)


ci_summary_overall1 <- ci_summary_overall1 %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "BW 2022",
    shore == "BW" & water_year == 2023 ~ "BW 2023",
    shore == "GB" & water_year == 2022 ~ "GB 2022",
    shore == "GB" & water_year == 2023 ~ "GB 2023",
    shore == "SS" & water_year == 2022 ~ "SS 2022",
    shore == "SS" & water_year == 2023 ~ "SS 2023",
    TRUE ~ "Other"
  ))

SEM_df_GPP_comb1 <- SEM_df_GPP_comb %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "Large inflow dry (WY 2022)",
    shore == "BW" & water_year == 2023 ~ "Large inflow wet (WY 2023)",
    shore == "GB" & water_year == 2022 ~ "Small inflow wet (WY 2023)",
    shore == "GB" & water_year == 2023 ~ "Small inflow dry (WY 2022)",
    shore == "SS" & water_year == 2022 ~ "No inflow dry (WY 2022)",
    shore == "SS" & water_year == 2023 ~ "No inflow wet (WY 2023)",
    TRUE ~ "Other"
  ))


SEM_df_GPP_comb1 <- SEM_df_GPP_comb1 %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_order)))

levels(SEM_df_GPP_comb1$Coefficient)
```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=9, fig.height=5}
# Violin plot of Estimate distributions per Coefficient
coef_violin_plot  <- ggplot(SEM_df_GPP_comb1, aes(
  y = Coefficient,
  x = Estimate,
  fill = point_shape,
  color = point_shape
)) +
    geom_violin(
    width = 2,
    alpha = 0.85,
    scale = "width",
    trim = FALSE,
    position = position_dodge(width = 0.5)  # Vertically dodges on y-axis
  ) +
  
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  theme(
    legend.position = "right",
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)

  ) +
    scale_color_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#216c8f", "Large inflow wet (WY 2023)" = "#216c8f",
                                "Small inflow dry (WY 2022)" = "#a67d17", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#09573e", "No inflow wet (WY 2023)" = "#09573e")) +
      scale_fill_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#d3e8f2", "Large inflow wet (WY 2023)" = "#3283a8",
                                "Small inflow dry (WY 2022)" = "#f5e5bc", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#cce3d6", "No inflow wet (WY 2023)" = "#136F63")) +

  labs(
    x = "Estimate",
    y = NULL,
    title = "GPP SEM Coefficients"
  ) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 5.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 3.5,  color = "gray40", linetype = "dotted") +
    geom_hline(yintercept = 1.5,  color = "gray40", linetype = "dotted") +

    theme(
    axis.text.y = element_text(size = 14),
    legend.position = "right"
  ) +
 # xlim(-0.85,0.85) +
    theme_minimal() +
    scale_y_discrete(labels = c(
    "b_plotGPP_plot_GPP_lag" = "Metab. ~ AR",
    "b_plotGPP_lake_tempC" = "Metab. ~ Temp.",
    "b_plotGPP_light_mean" = "Metab. ~ Light",
    "b_plotGPP_flow_mean" = "Metab. ~ Flow",
    "b_laketempC_flow_mean" = "Temp ~ Flow",
    "b_laketempC_ppt_mm" = "Temp ~ PPT",
    "b_lightmean_flow_mean" = "Light ~ Flow",
    "b_lightmean_ppt_mm" = "Light ~ PPT",
    "b_flowmean_ppt_mm" = "Flow ~ PPT"
  )) 


```

```{r, warning=F, size = 'small', echo=FALSE, include=FALSE}


SEM_BW22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_22_ER_final_logflow.rds") %>%
  mutate(water_year=2022)

SEM_BW23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_BW_23_ER_final_logflow.rds") %>%
  mutate(water_year=2023)

SEM_GB22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_22_ER_final_logflow.rds") %>%
  mutate(water_year=2022)

SEM_GB23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_GB_23_ER_final_logflow.rds") %>%
  mutate(water_year=2023)


## SSNS SEM output:
SEM_SS22e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_ER_22_final_v2.rds") %>%
  mutate(water_year=2022)

SEM_SS23e <-readRDS("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/posterior_samples_melted_SS_23_ER_final_v2.rds") %>%
  mutate(water_year=2023)

```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=8, fig.height=6}

SEM_df_ER_comb <- rbind(SEM_BW22e, SEM_GB22e, SEM_SS22e, 
                         SEM_BW23e, SEM_GB23e, SEM_SS23e)

ci_summary_overalle <- SEM_df_ER_comb %>%
  dplyr::group_by(Coefficient, shore, water_year) %>%
  dplyr:: summarize(
    median = median(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )

summary(SEM_df_ER_comb)


# write_csv(ci_summary_overalle, "/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/SEM_output/SEM_summary/SEM_CI_ER_logflow.csv")



ci_summary_overall_T <- SEM_df_ER_comb %>%
  dplyr::group_by(Coefficient, water_year) %>%
  dplyr:: summarize(
    median = median(Estimate),
    l_95 = quantile(Estimate, 0.025),
    u_95 = quantile(Estimate, 0.975),
    .groups = "drop"
  )


coef_ordere <- c(
  "b_plotER_plot_ER_lag",
  "b_plotER_lake_tempC",
  "b_plotER_light_mean",
  "b_plotER_flow_mean",
  "b_laketempC_flow_mean",
  "b_laketempC_ppt_mm",
  "b_lightmean_flow_mean",
  "b_lightmean_ppt_mm",
  "b_flowmean_ppt_mm"
)


ci_summary_overall1e<- ci_summary_overalle %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_ordere)))

levels(ci_summary_overall1$Coefficient)


ci_summary_overall1e <- ci_summary_overall1e %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "BW 2022",
    shore == "BW" & water_year == 2023 ~ "BW 2023",
    shore == "GB" & water_year == 2022 ~ "GB 2022",
    shore == "GB" & water_year == 2023 ~ "GB 2023",
    shore == "SS" & water_year == 2022 ~ "SS 2022",
    shore == "SS" & water_year == 2023 ~ "SS 2023",
    TRUE ~ "Other"
  ))



ci_summary_overall1 <- ci_summary_overall1 %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "BW 2022",
    shore == "BW" & water_year == 2023 ~ "BW 2023",
    shore == "GB" & water_year == 2022 ~ "GB 2022",
    shore == "GB" & water_year == 2023 ~ "GB 2023",
    shore == "SS" & water_year == 2022 ~ "SS 2022",
    shore == "SS" & water_year == 2023 ~ "SS 2023",
    TRUE ~ "Other"
  ))

SEM_df_ER_comb1 <- SEM_df_ER_comb %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "Large inflow dry (WY 2022)",
    shore == "BW" & water_year == 2023 ~ "Large inflow wet (WY 2023)",
    shore == "GB" & water_year == 2022 ~ "Small inflow wet (WY 2023)",
    shore == "GB" & water_year == 2023 ~ "Small inflow dry (WY 2022)",
    shore == "SS" & water_year == 2022 ~ "No inflow dry (WY 2022)",
    shore == "SS" & water_year == 2023 ~ "No inflow wet (WY 2023)",
    TRUE ~ "Other"
  ))


SEM_df_ER_comb1 <- SEM_df_ER_comb1 %>%
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_ordere)))

levels(SEM_df_GPP_comb1$Coefficient)

```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=8, fig.height=6}

####
coef_plot_er <- ggplot(ci_summary_overall1e, aes(x = median, y = Coefficient, 
                                                 color = point_shape, shape = point_shape)) +
  geom_point(position = position_dodge(width = 0.5), size = 3, alpha=0.9) +
  geom_errorbarh(aes(xmin = l_95, xmax = u_95),
                 position = position_dodge(width = 0.5), height = 0, alpha=0.45) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
  scale_color_manual(name = "Shore and water year", 
                     values = c("BW 2022" = "#3283a8", "BW 2023" = "#3283a8",
                                "GB 2022" = "#a67d17", "GB 2023" = "#a67d17",
                                "SS 2022" = "#136F63", "SS 2023" = "#136F63")) +
  
  scale_shape_manual(name = "Shore and water year",
                     values = c("BW 2022" = 1, "BW 2023" = 19, 
                                "GB 2022" = 2, "GB 2023" = 17, 
                                "SS 2022" = 0, "SS 2023" = 15)) +

  theme_minimal() +
  labs(
    x = "Posterior median ± 95% CI",
    y = NULL,
    title = "|ER|"
  ) +
  theme(
    axis.text.y = element_text(size = 10),
    legend.position = "right"
  ) + scale_y_discrete(labels=NULL)

coef_plot_er

#####


SEM_df_ER_comb <- SEM_df_ER_comb%>% 
  mutate(Coefficient = fct_relevel(Coefficient, rev(coef_ordere))) %>%
  mutate(point_shape = case_when(
    shore == "BW" & water_year == 2022 ~ "Large inflow dry (WY 2022)",
    shore == "BW" & water_year == 2023 ~ "Large inflow wet (WY 2023)",
    shore == "GB" & water_year == 2022 ~ "Small inflow dry (WY 2022)",
    shore == "GB" & water_year == 2023 ~ "Small inflow wet (WY 2023)",
    shore == "SS" & water_year == 2022 ~ "No inflow dry (WY 2022)",
    shore == "SS" & water_year == 2023 ~ "No inflow wet (WY 2023)",
    TRUE ~ "Other"
  ))



SEM_df_ER_comb$point_shape <- factor(
  SEM_df_ER_comb$point_shape,
  levels = c(
    "No inflow wet (WY 2023)",
    "No inflow dry (WY 2022)",
    "Small inflow wet (WY 2023)",
    "Small inflow dry (WY 2022)",
    "Large inflow wet (WY 2023)",
    "Large inflow dry (WY 2022)" # draw last = appear on top
  )
)


#
# Violin plot of Estimate distributions per Coefficient
coef_violin_plot_ER_fac <- ggplot(SEM_df_ER_comb1, aes(
  y = Coefficient,
  x = Estimate,
  fill = point_shape,
  color = point_shape
)) +
  geom_violin(
  width = 0.5,
  alpha = 0.85,
  scale = "width",
  trim = FALSE,
  position = position_identity()
)+
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  theme(
    legend.position = "right",
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)

  ) +
    scale_color_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#216c8f", "Large inflow wet (WY 2023)" = "#216c8f",
                                "Small inflow dry (WY 2022)" = "#a67d17", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#09573e", "No inflow wet (WY 2023)" = "#09573e")) +
      scale_fill_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#d3e8f2", "Large inflow wet (WY 2023)" = "#3283a8",
                                "Small inflow dry (WY 2022)" = "#f5e5bc", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#cce3d6", "No inflow wet (WY 2023)" = "#136F63")) +

  labs(
    x = "Estimate",
    y = NULL,
    title = "ER SEM Coefficients"
  ) +
   # xlim(-0.85,0.85) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
    theme(
    axis.text.y = element_text(size = 10),
    legend.position = "right"
  )  + scale_y_discrete(labels=NULL) +
    theme_minimal() + facet_grid(.~shore)
  #   +
  # scale_y_discrete(labels = c(
  #   "b_plotER_plot_ER_lag" = "Metab. ~ AR",
  #   "b_plotER_lake_tempC" = "Metab. ~ Temp.",
  #   "b_plotER_light_mean" = "Metab. ~ Light",
  #   "b_plotER_flow_mean" = "Metab. ~ Flow",
  #   "b_laketempC_flow_mean" = "Temp ~ Flow",
  #   "b_laketempC_log_ppt_mm_z" = "Temp ~ PPT",
  #   "b_lightmean_flow_mean" = "Light ~ Flow",
  #   "b_lightmean_log_ppt_mm_z" = "Light ~ PPT"
  # )) 




#
# Violin plot of Estimate distributions per Coefficient
coef_violin_plot_ER <- ggplot(SEM_df_ER_comb, aes(
  y = Coefficient,
  x = Estimate,
  fill = point_shape,
  color = point_shape
)) +
  geom_violin(
  width = 0.5,
  alpha = 0.85,
  scale = "width",
  trim = FALSE,
  position = position_identity()
)+
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  theme(
    legend.position = "right",
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)

  ) +
    scale_color_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#216c8f", "Large inflow wet (WY 2023)" = "#216c8f",
                                "Small inflow dry (WY 2022)" = "#a67d17", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#09573e", "No inflow wet (WY 2023)" = "#09573e")) +
      scale_fill_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#d3e8f2", "Large inflow wet (WY 2023)" = "#3283a8",
                                "Small inflow dry (WY 2022)" = "#f5e5bc", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#cce3d6", "No inflow wet (WY 2023)" = "#136F63")) +

  labs(
    x = "Estimate",
    y = NULL,
    title = "ER SEM Coefficients"
  ) +
   # xlim(-0.85,0.85) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
    theme(
    axis.text.y = element_text(size = 10),
    legend.position = "right"
  )  + scale_y_discrete(labels=NULL) +
    theme_minimal() 



coef_violin_plot_ER <- ggplot(SEM_df_ER_comb1, aes(
  y = Coefficient,
  x = Estimate,
  fill = point_shape,
  color = point_shape,
  group = interaction(Coefficient, point_shape)  # This groups violins for dodging
)) +
  geom_violin(
    width = 2,
    alpha = 0.85,
    scale = "width",
    trim = FALSE,
    position = position_dodge(width = 0.5)  # Vertically dodges on y-axis
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  theme_minimal() +
  theme(
    legend.position = "right",
    axis.text.y = element_text(size = 14),
    plot.title = element_text(hjust = 0.5)
  ) +
  scale_color_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#216c8f", "Large inflow wet (WY 2023)" = "#216c8f",
                                "Small inflow dry (WY 2022)" = "#a67d17", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#09573e", "No inflow wet (WY 2023)" = "#09573e")) +
  scale_fill_manual(name = "Flow regime and water year", 
                     values = c("Large inflow dry (WY 2022)" = "#d3e8f2", "Large inflow wet (WY 2023)" = "#3283a8",
                                "Small inflow dry (WY 2022)" = "#f5e5bc", "Small inflow wet (WY 2023)" = "#a67d17",
                                "No inflow dry (WY 2022)" = "#cce3d6", "No inflow wet (WY 2023)" = "#136F63")) +
  labs(
    x = "Estimate",
    y = NULL,
    title = "ER SEM Coefficients"
  ) +
  geom_hline(yintercept = 5.5, color = "gray40", linetype = "dotted") +
  geom_hline(yintercept = 3.5, color = "gray40", linetype = "dotted") +
    geom_hline(yintercept = 1.5, color = "gray40", linetype = "dotted") +

  scale_y_discrete(labels = NULL)




```

### Part of revised Figure 3 

The DAG is drawn in power point. 

#### SEM as coeff plot:
Draft with both GPP and ER

```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=15, fig.height=7}

SEM_grid <- ggarrange(
  coef_violin_plot,
  coef_violin_plot_ER,
  #labels = c("b", "c"),
 # align=c("v"),
 # label.x = 0.9,
  #label.y = 1,
 common.legend = T,
   legend = "bottom",
 # hjust = 0.1,
  #vjust = 1,
  widths = c(1, 0.85),
  ncol = 2, nrow = 1)

SEM_grid

```


```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Revised_coeff_Fig3_v2_logflow.png", plot = SEM_grid, width = 8, height = 6, units = "in")

```



#### SEM as coeff shore faceted plot:
Draft with both GPP and ER

```{r, warning=F, size = 'small', echo=FALSE, include=T, fig.width=15, fig.height=7}

SEM_grid <- ggarrange(
  coef_violin_plot_fac,
  coef_violin_plot_ER_fac,
  #labels = c("b", "c"),
 # align=c("v"),
 # label.x = 0.9,
  #label.y = 1,
 common.legend = T,
   legend = "bottom",
 # hjust = 0.1,
  #vjust = 1,
  widths = c(1, 0.85),
  ncol = 2, nrow = 1)

SEM_grid

```


```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Revised_coeff_Fig3_faceted.png", plot = SEM_grid, width = 12, height = 4.5, units = "in")

```






```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=8, fig.height=6}
library(ggridges)

### SEM as density plot 

# Reorder Coefficients for plotting
SEM_df_GPP_comb <- SEM_df_GPP_comb %>%
  mutate(
    Coefficient = fct_relevel(Coefficient, rev(coef_order)),
    point_shape = case_when(
      shore == "BW" & water_year == 2022 ~ "BW 2022",
      shore == "BW" & water_year == 2023 ~ "BW 2023",
      shore == "GB" & water_year == 2022 ~ "GB 2022",
      shore == "GB" & water_year == 2023 ~ "GB 2023",
      shore == "SS" & water_year == 2022 ~ "SS 2022",
      shore == "SS" & water_year == 2023 ~ "SS 2023",
      TRUE ~ "Other"
    )
  )


ridge_plot <- ggplot(SEM_df_GPP_comb, aes(x = Estimate, y = Coefficient, 
                                          fill = point_shape, color = point_shape)) +
  geom_density_ridges(scale = 0.75, alpha = 0.75, linewidth = 0.3, panel_scaling = TRUE) +
  scale_fill_manual(name = "Shore and water year", 
                    values = c("BW 2022" = "#3283a8", "BW 2023" = "white",
                               "GB 2022" = "#a67d17", "GB 2023" = "white",
                               "SS 2022" = "#136F63", "SS 2023" = "white")) +
  scale_color_manual(name = "Shore and water year", 
                     values = c("BW 2022" = "#3283a8", "BW 2023" = "#3283a8",
                                "GB 2022" = "#a67d17", "GB 2023" = "#a67d17",
                                "SS 2022" = "#136F63", "SS 2023" = "#136F63")) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
 # geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  #geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
  theme_minimal() +
  labs(
    x = "Estimate posterior",
    y = NULL,
    title = "GPP"
  ) +
  xlim(-4,1.3) +
  theme(
    axis.text.y = element_text(size = 8),
    axis.text.x = element_text(size = 8),
          axis.title.x = element_text(size = 8),
              axis.title.y = element_text(size = 8),
    legend.position = "right"
  ) +
  scale_y_discrete(labels = c(
    "b_plotGPP_plot_GPP_lag" = "Metab. ~ AR",
    "b_plotGPP_lake_tempC" = "Metab. ~ Temp.",
    "b_plotGPP_light_mean" = "Metab. ~ Light",
    "b_plotGPP_flow_mean" = "Metab. ~ Flow",
    "b_laketempC_flow_mean" = "Temp ~ Flow",
    "b_laketempC_ppt_mm" = "Temp ~ PPT",
    "b_lightmean_flow_mean" = "Light ~ Flow",
    "b_lightmean_ppt_mm" = "Light ~ PPT"
  ))


ridge_plot
```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=5, fig.height=6}
# Reorder Coefficients for plotting
SEM_df_ER_comb <- SEM_df_ER_comb %>%
  mutate(
    Coefficient = fct_relevel(Coefficient, rev(coef_ordere)),
    point_shape = case_when(
      shore == "BW" & water_year == 2022 ~ "BW 2022",
      shore == "BW" & water_year == 2023 ~ "BW 2023",
      shore == "GB" & water_year == 2022 ~ "GB 2022",
      shore == "GB" & water_year == 2023 ~ "GB 2023",
      shore == "SS" & water_year == 2022 ~ "SS 2022",
      shore == "SS" & water_year == 2023 ~ "SS 2023",
      TRUE ~ "Other"
    )
  )


library(ggridges)

ER_ridge_plot <- ggplot(SEM_df_ER_comb, aes(x = Estimate, y = Coefficient, 
                                          fill = point_shape, color = point_shape)) +
  geom_density_ridges(scale = 0.75, alpha = 0.75, linewidth = 0.3, panel_scaling = TRUE) +
  scale_fill_manual(name = "Shore and water year", 
                    values = c("BW 2022" = "#3283a8", "BW 2023" = "white",
                               "GB 2022" = "#a67d17", "GB 2023" = "white",
                               "SS 2022" = "#136F63", "SS 2023" = "white")) +
  scale_color_manual(name = "Shore and water year", 
                     values = c("BW 2022" = "#3283a8", "BW 2023" = "#3283a8",
                                "GB 2022" = "#a67d17", "GB 2023" = "#a67d17",
                                "SS 2022" = "#136F63", "SS 2023" = "#136F63")) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
 # geom_hline(yintercept = 4.5, color = "gray40", linetype = "dotted") +
  #geom_hline(yintercept = 2.5,  color = "gray40", linetype = "dotted") +
  theme_minimal() +
  labs(
    x = "Estimate posterior",
    y = NULL,
    title = "|ER|"
  ) +
    xlim(-4,1.3) +
  theme(
    axis.text.y = element_text(size = 8),
    legend.position = "right"
  ) +
    theme(
    axis.text.x = element_text(size = 8),
      axis.title.x = element_text(size = 8),
    legend.position = "right") + scale_y_discrete(labels=NULL)

ER_ridge_plot

```

```{r, warning=F, echo=FALSE, include=F, fig.width=10, fig.height=7}

SEM_grid <- ggarrange(
  ridge_plot,
  ER_ridge_plot,
 # labels = c("a", "b"),
 # align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
 common.legend = T,
   legend = "bottom",
  #hjust = 0.1,
  #vjust = 1,
 widths = c(1, 0.65),
 ncol = 2, nrow = 1)

SEM_grid

```




```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Revised_Fig3.png", plot = SEM_grid, width = 4.5, height = 5, units = "in")

```


```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=5, fig.height=6}

#### Supplemental figures:

# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_BW <- dat %>%
  filter(shore == "BW")

summary(GPP_df_BW)
# date range 2021-06-11  to 2023-09-14   


BW_GPP_df21 <- GPP_df_BW %>%
  filter(date > as.Date("2021-06-10") & date < as.Date("2021-09-10"))

summary(BW_GPP_df21)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO <- GPP_df_BW %>%
  filter(!is.na(lake_DO)) %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         yday=yday(date),
         year=year(date))

# Identify the unique yday values for each year
yday_2021 <- unique(plot_data_DO$yday[plot_data_DO$year == 2021])
yday_2022 <- unique(plot_data_DO$yday[plot_data_DO$year == 2022])
yday_2023 <- unique(plot_data_DO$yday[plot_data_DO$year == 2023])

# Find the common yday values across all three years
common_yday <- Reduce(intersect, list(#yday_2021, 
                                      yday_2022, 
                                      yday_2023))

# Filter the dataframe for only those common yday values
filtered_data_BW_d <- plot_data_DO %>%
  filter(yday %in% common_yday & year %in% c(2022, 2023))

filtered_data_BW_cs <- filtered_data_BW_d%>%
  arrange(year, yday) %>%
  group_by(year) %>%
  mutate(GPPcumsum = cumsum(plot_GPP))

# Determine the date range
date_range <- range(plot_data_DO$date, na.rm = TRUE)


# Create the number line plot
templt_BW <- ggplot(plot_data_DO, aes(x = date)) +
  #geom_segment(aes(x = date_range[1], xend = date_range[2], y = 0, yend = 0), linewidth = 0.2) + # Main line
  geom_point(data = filter(plot_data_DO, has_do), aes(y = 0.095), alpha=0.8, color = "black", size = 1) + 
  geom_point(data = filter(filtered_data_BW_d, has_GPP), aes(y = 0.090), alpha= 0.8, color = "#579467", size = 1) + 
  scale_y_continuous(name = "", breaks = NULL) +
  theme_classic() + xlab(NULL) +
  scale_x_date(date_breaks = "8 week",date_labels = "%b-%y", limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))) +
  labs(title = "BW NS1-3 metab.") #+facet_grid(year~.)

```




```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=5, fig.height=6}
# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_GB <- dat%>%
  filter(shore == "GB")

summary(GPP_df_GB)
# date range 2021-06-11  to 2023-09-14   


GB_GPP_df21 <- GPP_df_GB %>%
  filter(date > as.Date("2021-06-10") & date < as.Date("2021-09-10"))

summary(GB_GPP_df21)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO <- GPP_df_GB %>%
  filter(!is.na(lake_DO)) %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         yday=yday(date),
         year=year(date))

# Identify the unique yday values for each year
yday_2021 <- unique(plot_data_DO$yday[plot_data_DO$year == 2021])
yday_2022 <- unique(plot_data_DO$yday[plot_data_DO$year == 2022])
yday_2023 <- unique(plot_data_DO$yday[plot_data_DO$year == 2023])

# Find the common yday values across all three years
common_yday <- Reduce(intersect, list(#yday_2021, 
                                      yday_2022, 
                                      yday_2023))

# Filter the dataframe for only those common yday values
filtered_data_GB_d <- plot_data_DO %>%
  filter(yday %in% common_yday & year %in% c(2022, 2023))

filtered_data_cs <- filtered_data%>%
  arrange(year, yday) %>%
  group_by(year) %>%
  mutate(GPPcumsum = cumsum(plot_GPP))

# Determine the date range
date_range <- range(plot_data_DO$date, na.rm = TRUE)


# Create the number line plot
templt_GB <- ggplot(plot_data_DO, aes(x = date)) +
  #geom_segment(aes(x = date_range[1], xend = date_range[2], y = 0, yend = 0), linewidth = 0.2) + # Main line
  geom_point(data = filter(plot_data_DO, has_do), aes(y = 0.095), alpha=0.8, color = "black", size = 1) + # DO presence tick marks
  geom_point(data = filter(filtered_data_GB_d, has_GPP), aes(y = 0.090), alpha= 0.8, color = "#579467", size = 1) + # GPP presence tick marks
  scale_y_continuous(name = "", breaks = NULL) +
    scale_x_date(date_breaks = "8 week",date_labels = "%b-%y", limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))) +
  theme_classic() + xlab(NULL) +
  labs(title = "GB NS1-3 metab.") #+facet_grid(year~.)

```





```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=5, fig.height=6}
# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_SS <- dat%>%
  filter(shore == "SS")

summary(GPP_df_SS)
# date range 2021-06-11  to 2023-09-14   


SS_GPP_df21 <- GPP_df_SS %>%
  filter(date > as.Date("2021-06-10") & date < as.Date("2021-09-10"))

summary(SS_GPP_df21)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO <- GPP_df_SS %>%
  filter(!is.na(lake_DO)) %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         yday=yday(date),
         year=year(date))

# Identify the unique yday values for each year
yday_2021 <- unique(plot_data_DO$yday[plot_data_DO$year == 2021])
yday_2022 <- unique(plot_data_DO$yday[plot_data_DO$year == 2022])
yday_2023 <- unique(plot_data_DO$yday[plot_data_DO$year == 2023])

# Find the common yday values across all three years
common_yday <- Reduce(intersect, list(#yday_2021, 
                                      yday_2022, 
                                      yday_2023))

# Filter the dataframe for only those common yday values
filtered_data_SS_d <- plot_data_DO %>%
  filter(yday %in% common_yday & year %in% c(2022, 2023))

filtered_data_cs <- filtered_data%>%
  arrange(year, yday) %>%
  group_by(year) %>%
  mutate(GPPcumsum = cumsum(plot_GPP))

# Determine the date range
date_range <- range(plot_data_DO$date, na.rm = TRUE)


# Create the number line plot
templt_SS <- ggplot(plot_data_DO, aes(x = date)) +
  #geom_segment(aes(x = date_range[1], xend = date_range[2], y = 0, yend = 0), linewidth = 0.2) + # Main line
  geom_point(data = filter(plot_data_DO, has_do), aes(y = 0.095), alpha=0.8, color = "black", size = 1) + # DO presence tick marks
  geom_point(data = filter(filtered_data_SS_d, has_GPP), aes(y = 0.090), alpha= 0.8, color = "#579467", size = 1) + # GPP presence tick marks
  scale_y_continuous(name = "", breaks = NULL) +
  theme_classic() + xlab(NULL) +
    scale_x_date(
       limits = c(as.Date("2021-09-29"), as.Date("2023-10-01")),
      date_breaks = "8 week", date_labels = "%b-%y") +
  labs(title = "SS NS1 & 2 metab.") #+facet_grid(year~.)

```



```{r, warning=F, size = 'small', echo=FALSE, include=F, fig.width=5, fig.height=6}
# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_SH <- dat%>%
  filter(shore == "SH")

summary(GPP_df_SH)
# date range 2021-06-11  to 2023-09-14   


SH_GPP_df21 <- GPP_df_SH %>%
  filter(date > as.Date("2021-06-10") & date < as.Date("2021-09-10"))

summary(SH_GPP_df21)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO <- GPP_df_SH %>%
  filter(!is.na(lake_DO)) %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         yday=yday(date),
         year=year(date))

# Identify the unique yday values for each year
yday_2021 <- unique(plot_data_DO$yday[plot_data_DO$year == 2021])
yday_2022 <- unique(plot_data_DO$yday[plot_data_DO$year == 2022])
yday_2023 <- unique(plot_data_DO$yday[plot_data_DO$year == 2023])

# Find the common yday values acroSH all three years
common_yday <- Reduce(intersect, list(#yday_2021, 
                                      yday_2023))

# Filter the dataframe for only those common yday values
filtered_data_SH_d <- plot_data_DO %>%
  filter(yday %in% common_yday & year %in% c(2023))

filtered_data_cs <- filtered_data%>%
  arrange(year, yday) %>%
  group_by(year) %>%
  mutate(GPPcumsum = cumsum(plot_GPP))

# Determine the date range
date_range <- range(plot_data_DO$date, na.rm = TRUE)


# Create the number line plot
templt_SH <- ggplot(plot_data_DO, aes(x = date)) +
  #geom_segment(aes(x = date_range[1], xend = date_range[2], y = 0, yend = 0), linewidth = 0.2) + # Main line
  geom_point(data = filter(plot_data_DO, has_do), aes(y = 0.095), alpha=0.8, color = "black", size = 1) + # DO presence tick marks
  geom_point(data = filter(filtered_data_SH_d, has_GPP), aes(y = 0.090), alpha= 0.8, color = "#579467", size = 1) + # GPP presence tick marks
  scale_y_continuous(name = "", breaks = NULL) +
  theme_classic() + xlab(NULL) +
      scale_x_date(
       limits = c(as.Date("2021-09-29"), as.Date("2023-10-01")),
      date_breaks = "8 week", date_labels = "%b-%y") +
  labs(title = "SH NS1-3 metab.") #+facet_grid(year~.)

```


#### Supplemental figures:

Overlapping observations of DO (black) and metabolism estimates (green).


```{r, warning=F, echo=FALSE, include=T, fig.width=8, fig.height=3.5}

SEM_grid <- ggarrange(
  templt_BW,
  templt_GB,
  templt_SS,
  templt_SH,
 # align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
  #hjust = 0.1,
  #vjust = 1,
 ncol = 1, nrow = 4)

SEM_grid

```


```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Sup_Fig_nearshore_dat_resolution.png", plot = SEM_grid, width = 7, height = 3.25, units = "in")

```


### Question 2

How does ecosystem metabolism and environmental conditions in the nearshore of the lake change between paired locations with and without stream inflows?


#### Looking into the shore differences in metabolism between shores near and far from streams:



```{r, warning=F, size = 'small', echo=F, include=FALSE}

dat <-readRDS("/Users/kellyloria/Documents/UNR/MSMmetab/SFS24_Analysis/Final_Scripts/NS_analysis_dat.rds") %>%
  mutate(middle_ER_ab = c(middle_ER*-1))


chem_dat <- readRDS("/Users/kellyloria/Documents/UNR/MSMmetab/SFS24_Analysis/Final_Scripts/NS_chem_dat.rds")
unique(chem_dat$site)
summary(chem_dat) 

OM_dat <- read.csv("/Users/kellyloria/Documents/UNR/MSMmetab/Sediment_OM_dat.csv") %>%
  mutate(date=as.Date(date, format("%m/%d/%y"))) %>%
  filter(Site=="GB_NS1" | Site=="GB_NS2" | Site=="GB_NS3" |
           Site=="BWNS1" |  Site=="BWNS2" | Site=="BWNS3" |
           Site=="SSNS1" |  Site=="SSNS2" | Site=="SSNS3" |
           Site=="SHNS1" |  Site=="SHNS2" | Site=="SHNS3") %>%
  dplyr::group_by(shore, date) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE))

pdat <-dat %>%
  dplyr::select(-X, -Latitude, -Longitude, elevation_m) %>%  # drop the 'date' column
  left_join(chem_dat, by=c("date", "shore", "site", "WaterYear")) %>%
  left_join(OM_dat, by=c("date", "shore"))


week_dat <- pdat %>%
  dplyr::select(-yday) %>%  # drop the 'date' column
  dplyr::group_by(site, shore, week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

```

##### Whole time sieries 

Weekly averages by shore

```{r, warning=F, echo=FALSE, include=T, fig.width=10, fig.height=7}
TS_plots <- ggplot(week_dat, aes(y = middle_GPP, x = week, color = as.factor(shore), shape=shore)) +
    geom_point(aes(x = week, y = middle_GPP), size = 2, alpha = 0.75) +
    geom_smooth(aes(group = as.factor(shore), fill = as.factor(shore)), 
            se = TRUE, linewidth = 1, method = "gam", formula = y ~ s(x, k = 10), alpha = 0.1)+
  theme_classic() +
    scale_fill_manual(name="Shore",
    values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
  scale_color_manual(name="Shore",
    values = c(SS = "#136F63", BW = "#3283a8", GB = "#a67d17", SH = "#c76640")) +
  ylim(-5,45) + scale_shape_manual(values = c(SS = 1, BW = 19, GB = 17, SH= 2)) +
 ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  xlab("Week number") +
  labs(title="All shores") +facet_grid(WaterYear~.)

TS_plots
```

2023 overlapping weeks from west shore locations week 3 - 41

```{r, warning=F, size = 'small', echo=F, include=FALSE}
df_BW_p <- week_dat %>%
  filter(shore == "BW") %>%
  filter(year==2023) %>%
  filter(week>4 & week<41) %>%
  dplyr::group_by(shore, week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop") %>%
  mutate(date=as.Date(date))%>%
  mutate(ER_abs = middle_ER*-1)


 df_SS_p <- week_dat %>%
  filter(shore == "SS") %>%
   filter(year==2023) %>%
   filter(week>4 & week<41)  %>%
   dplyr::group_by(shore, week, WaterYear) %>%
   dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop") %>%
     mutate(date=as.Date(date))%>%
  mutate(ER_abs = middle_ER*-1)
 
```

 
```{r, warning=F, echo=FALSE, include=F, fig.width=8, fig.height=3}
West_TS_plots <- ggplot(week_dat%>%filter(WaterYear==2023), aes(y = middle_GPP, x = date, color = as.factor(shore), shape=shore)) +
  geom_point(data = df_BW_p, aes(x = date, y = middle_GPP), color = "#3283a8", size = 2) +
  geom_point(data = df_SS_p, aes(x = date, y = middle_GPP), color = "#136F63", size = 2) +
  #geom_line(data = df_SS_p, aes(x = week, y = middle_GPP),color = "red") +
  #scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  scale_x_date(
  date_breaks = "3 week",
  date_labels = "%d-%b"
  #limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))
  ) +
 ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  labs(title="West shore") +
  xlab(NULL) +
  geom_smooth(data = df_BW_p, 
              se = TRUE, linewidth = 1, method = "gam", formula = y ~ s(x, k = 10), alpha = 0.1, color="#3283a8", fill="#3283a8") +
  geom_smooth(data = df_SS_p, 
              se = TRUE, linewidth = 1, method = "gam", formula = y ~ s(x, k = 10), alpha = 0.1, color="#136F63", fill= "#136F63") +
  theme_classic() + facet_grid(WaterYear~.)


West_TS_plots
```


```{r, warning=F, echo=FALSE, include=F, fig.width=8, fig.height=3}
df_GB_p <- week_dat %>%
  filter(shore == "GB") %>%
  filter(year==2023) %>%
  filter(week>5 & week<41)  %>%
  dplyr::group_by(shore, week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop") %>%
       mutate(date=as.Date(date))%>%
  mutate(ER_abs = middle_ER*-1)

df_SH_p <- week_dat %>%
  filter(shore == "SH") %>%
  filter(year==2023) %>%
  filter(week>5 & week<41)  %>%
  dplyr::group_by(shore, week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")%>%
       mutate(date=as.Date(date)) %>%
  mutate(ER_abs = middle_ER*-1)


East_TS_plots <- ggplot(week_dat%>%filter(WaterYear==2023), aes(y = (middle_GPP), x = date, color = as.factor(shore), shape=shore)) +
  geom_point(data = df_GB_p, aes(x = date, y = middle_GPP), color = "#a67d17", size = 2) +
  geom_point(data = df_SH_p, aes(x = date, y = middle_GPP), color = "#c86640", size = 2) +
  #scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
   ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
    scale_x_date(
  date_breaks = "3 week",
  date_labels = "%d-%b"
  #limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))
  ) +
  labs(title="East shore") +
  geom_smooth(data = df_GB_p, 
              se = TRUE, linewidth = 1, method = "gam", formula = y ~ s(x, k = 10), alpha = 0.1, color="#a67d17", fill="#a67d17") +
  geom_smooth(data = df_SH_p, 
              se = TRUE, linewidth = 1, method = "gam", formula = y ~ s(x, k = 10), alpha = 0.1, color="#c76640", fill="#c76640") +
  theme_classic() + facet_grid(WaterYear~.)

East_TS_plots

```



```{r, warning=F, echo=F, include=F, fig.width=10, fig.height=6}

png("./WY_GPP_panel_plot.png", width = 1550, height = 1250, res = 150)

# Set layout to 2 rows, 1 column
par(mfrow = c(2, 1),         # 2 rows, 1 column
    oma = c(1, 1, 1, 1),     # outer margin space
    mar = c(4, 5, 2, 8))  

# === FIRST PLOT (East shore) ===
plot(df_GB_p$date, df_GB_p$middle_GPP, type = "p", pch = 16, col = "#a67d17",
     xaxt = "n", xlab = "", ylab = expression(GPP~(mmol~O[2]~m^-3~d^-1)),
     ylim = c(-2.5, 25), main = "East shore")
tick_dates <- seq(from = min(df_GB_p$date), to = max(df_GB_p$date), by = "3 weeks")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_SH_p$date, df_SH_p$middle_GPP, pch = 17, col = "#c86640")

# GAM smooths
library(mgcv)
gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_GB_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SH_p)
date_seq <- seq(min(df_GB_p$date), max(df_GB_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#a67d17", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#c86640", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#a67d17", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#c86640", alpha.f = 0.2), border = NA)

# Flow and PPT on right
par(new = TRUE)
flow_ylim <- rev(range(df_GB_p$flow_mean, na.rm = TRUE) + c(0, 0.75 * diff(range(df_GB_p$flow_mean, na.rm = TRUE))))
plot(df_GB_p$date, df_GB_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")

par(new = TRUE)
ppt_ylim <- rev(c(0, max(df_GB_p$ppt_mm, na.rm = TRUE)+5))
plot(df_GB_p$date, df_GB_p$ppt_mm, type = "l", col = "#6fded7", lwd = 3, lty=2,
     axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)
axis(4, at = pretty(df_GB_p$ppt_mm), labels = pretty(df_GB_p$ppt_mm), line = 5.5, col.axis = "#6fded7", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 7.5, col = "#6fded7")

legend("bottomright", inset = c(-0.05, -0.05), xpd = TRUE,
       legend = c("GB: Small inflow", "SH: No inflow", "Flow", "PPT"), 
       col = c("#a67d17", "#c86640", "#448ff2", "#6fded7"), 
       pch = c(16, 17, NA, NA), 
       lwd = c(NA, NA, 3, 3), 
       lty = c(NA, NA, 3, 2),
       y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)

# === SECOND PLOT (West shore) ===

# par(oma = c(1, 1, 1, 1),    
#     mar = c(4, 5, 2, 8))  

plot(df_BW_p$date, df_BW_p$middle_GPP, type = "p", pch = 16, col = "#3283a8",
     xaxt = "n", xlab = "Date", ylab = expression(GPP~(mmol~O[2]~m^-3~d^-1)),
     ylim = c(-2.5, 35), main = "West shore")
tick_dates <- seq(from = min(df_BW_p$date), to = max(df_BW_p$date), by = "3 weeks")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_SS_p$date, df_SS_p$middle_GPP, pch = 17, col = "#136F63")

gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_BW_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SS_p)
date_seq <- seq(min(df_BW_p$date), max(df_BW_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#3283a8", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#136F63", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#3283a8", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#136F63", alpha.f = 0.2), border = NA)

par(new = TRUE)
flow_ylim <- rev(range(df_BW_p$flow_mean, na.rm = TRUE) + c(0, 0.75 * diff(range(df_BW_p$flow_mean, na.rm = TRUE))))
plot(df_BW_p$date, df_BW_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")

par(new = TRUE)
ppt_ylim <- rev(c(0, max(df_BW_p$ppt_mm, na.rm = TRUE)+5))
plot(df_BW_p$date, df_BW_p$ppt_mm, type = "l", col = "#6fded7", lwd = 3, lty=2,
     axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)
axis(4, at = pretty(df_BW_p$ppt_mm), labels = pretty(df_BW_p$ppt_mm), line = 5.5, col.axis = "#6fded7", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 7.5, col = "#6fded7")


legend("bottomright", inset = c(-0.05, -0.05), xpd = TRUE,
       legend = c("BW: Large inflow", "SS: No inflow", "Flow", "PPT"), 
       col = c("#3283a8", "#136F63", "#448ff2", "#6fded7"), 
       pch = c(16, 17, NA, NA), 
       lwd = c(NA, NA, 3, 3), 
       lty = c(NA, NA, 3, 2),
       y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)


dev.off()
```




```{r, warning=F, echo=F, include=F, fig.width=10, fig.height=6}

#png("./WY_Metab_panel_plot.png", width = 1550, height = 1300, res = 150)

# Set layout to 2 rows, 1 column
par(mfrow = c(2, 1),         # 2 rows, 1 column
    oma = c(1, 1, 1, 1),     # outer margin space
    mar = c(4, 5, 2, 8))  

# === FIRST PLOT (East shore) ===
plot(df_GB_p$date, df_GB_p$middle_GPP, type = "p", pch = 16, col = "#a67d17",
     xaxt = "n", xlab = "", ylab ="",
     ylim = c(-12.5, 25), main = "East shore")
tick_dates <- seq(from = min(df_GB_p$date), to = max(df_GB_p$date), by = "3 weeks")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_GB_p$date, df_GB_p$middle_ER, pch = 1, col = "#a67d17")
abline(h = 0, col = "black", lwd = 1)
mtext( expression(Metabolism~(mmol~O[2]~m^-3~d^-1)), side = 2, line = 2, col = "black")



points(df_SH_p$date, df_SH_p$middle_GPP, pch = 17, col = "#c86640")
points(df_SH_p$date, df_SH_p$middle_ER, pch = 2, col = "#c86640")


# GAM smooths
library(mgcv)
gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_GB_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SH_p)
date_seq <- seq(min(df_GB_p$date), max(df_GB_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#a67d17", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#c86640", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#a67d17", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#c86640", alpha.f = 0.2), border = NA)


gam_gb_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_GB_p)
gam_sh_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_SH_p)
date_seq_e <- seq(min(df_GB_p$date), max(df_GB_p$date), by = "1 day")
pred_gb_e <- predict(gam_gb_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
pred_sh_e <- predict(gam_sh_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
lines(date_seq_e, pred_gb_e$fit, col = "#a67d17", lwd = 2)
lines(date_seq_e, pred_sh_e$fit, col = "#c86640", lwd = 2)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_gb_e$fit + 2*pred_gb_e$se.fit, rev(pred_gb_e$fit - 2*pred_gb_e$se.fit)),
        col = adjustcolor("#a67d17", alpha.f = 0.2), border = NA)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_sh_e$fit + 2*pred_sh_e$se.fit, rev(pred_sh_e$fit - 2*pred_sh_e$se.fit)),
        col = adjustcolor("#c86640", alpha.f = 0.2), border = NA)


# Flow and PPT on right
par(new = TRUE)
flow_ylim <- rev(range(df_GB_p$flow_mean, na.rm = TRUE) + c(0, 1.25 * diff(range(df_GB_p$flow_mean, na.rm = TRUE))))
plot(df_GB_p$date, df_GB_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")



par(new = TRUE)
ppt_max <- max(df_GB_p$ppt_mm, na.rm = TRUE)
ppt_ylim <- rev(c(0, ppt_max * 2.3))  # or use + fixed offset, e.g., ppt_max + 50

plot(df_GB_p$date, df_GB_p$ppt_mm, type = "l", col = "#6fded7", lwd = 3, lty = 2,
     axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)

axis(4,
     at = pretty(ppt_ylim), 
     labels = pretty(ppt_ylim),
     line = 3.75, col.axis = "#6fded7", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 5.75, col = "#6fded7")


legend("bottom", inset = c(-0.05, -0.05), xpd = TRUE,
       legend = c("Small inflow", "No inflow", "Streamflow", "Precipitation"), 
       col = c("#a67d17", "#c86640", "#448ff2", "#6fded7"), 
       pch = c(16, 17, NA, NA), 
       lwd = c(NA, NA, 3, 3), 
       lty = c(NA, NA, 3, 2),
       y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)

# === SECOND PLOT (West shore) ===

# par(oma = c(1, 1, 1, 1),    
#     mar = c(4, 5, 2, 8))  

plot(df_BW_p$date, df_BW_p$middle_GPP, type = "p", pch = 16, col = "#3283a8",
     xaxt = "n", xlab = "Date", ylab = "",
     ylim = c(-30, 35), main = "West shore")
tick_dates <- seq(from = min(df_BW_p$date), to = max(df_BW_p$date), by = "3 weeks")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_SS_p$date, df_SS_p$middle_GPP, pch = 17, col = "#136F63")
points(df_BW_p$date, df_BW_p$middle_ER, pch = 1, col = "#3283a8")
points(df_SS_p$date, df_SS_p$middle_ER, pch = 2, col = "#136F63")
abline(h = 0, col = "black", lwd = 1)
mtext( expression(Metabolism~(mmol~O[2]~m^-3~d^-1)), side = 2, line = 2, col = "black")



gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_BW_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SS_p)
date_seq <- seq(min(df_BW_p$date), max(df_BW_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#3283a8", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#136F63", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#3283a8", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#136F63", alpha.f = 0.2), border = NA)




gam_gb_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_BW_p)
gam_sh_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_SS_p)
date_seq_e <- seq(min(df_BW_p$date), max(df_BW_p$date), by = "1 day")
pred_gb_e <- predict(gam_gb_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
pred_sh_e <- predict(gam_sh_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
lines(date_seq, pred_gb_e$fit, col = "#3283a8", lwd = 2)
lines(date_seq, pred_sh_e$fit, col = "#136F63", lwd = 2)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_gb_e$fit + 2*pred_gb_e$se.fit, rev(pred_gb_e$fit - 2*pred_gb_e$se.fit)),
        col = adjustcolor("#3283a8", alpha.f = 0.2), border = NA)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_sh_e$fit + 2*pred_sh_e$se.fit, rev(pred_sh_e$fit - 2*pred_sh_e$se.fit)),
        col = adjustcolor("#136F63", alpha.f = 0.2), border = NA)

par(new = TRUE)
flow_ylim <- rev(range(df_BW_p$flow_mean, na.rm = TRUE) + c(0, 1.25 * diff(range(df_BW_p$flow_mean, na.rm = TRUE))))
plot(df_BW_p$date, df_BW_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")
# 
# par(new = TRUE)
# ppt_ylim <- rev(c(0, max(df_BW_p$ppt_mm, na.rm = TRUE)+15))
# plot(df_BW_p$date, df_BW_p$ppt_mm, type = "l", col = "#6fded7", lwd = 3, lty=2,
#      axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)
# axis(4, at = pretty(df_BW_p$ppt_mm), labels = pretty(df_BW_p$ppt_mm), line = 5, col.axis = "#6fded7", col = "black")
# mtext(expression("Precipitation (mm)"), side = 4, line = 7.25, col = "#6fded7")




par(new = TRUE)
ppt_max <- max(df_BW_p$ppt_mm, na.rm = TRUE)
ppt_ylim <- rev(c(0, ppt_max * 2.3))  # or use + fixed offset, e.g., ppt_max + 50

plot(df_BW_p$date, df_BW_p$ppt_mm, type = "l", col = "#6fded7", lwd = 3, lty = 2,
     axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)

axis(4,
     at = pretty(ppt_ylim), 
     labels = pretty(ppt_ylim),
     line = 3.75, col.axis = "#6fded7", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 5.75, col = "#6fded7")

# 
# legend("bottom", inset = c(-0.05, -0.05), xpd = TRUE,
#        legend = c("Large inflow", "No inflow", "Streamflow", "Precipitation"), 
#        col = c("#3283a8", "#136F63", "#448ff2", "#6fded7"), 
#        pch = c(16, 17, NA, NA), 
#        lwd = c(NA, NA, 3, 3), 
#        lty = c(NA, NA, 3, 2),
#        y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)


dev.off()
```




```{r, warning=F, echo=F, include=T, fig.width=10, fig.height=8}

#
#png("./WY_Metab_panel_plot.png", width = 1550, height = 1250, res = 150)

xlim_range <- as.Date(c("2023-01-30", "2023-09-08"))  # adjust year if needed
tick_dates <- seq(from = xlim_range[1], to = xlim_range[2], by = "3 weeks")


# Set layout to 2 rows, 1 column
par(mfrow = c(2, 1),         # 2 rows, 1 column
    oma = c(1, 1, 1, 1),     # outer margin space
    mar = c(4, 5, 2, 8))  

# === FIRST PLOT (East shore) ===
plot(df_GB_p$date, df_GB_p$middle_GPP, type = "p", pch = 16, col = "#a67d17",
     xaxt = "n", xlab = "", ylab = "",
     ylim = c(-12.5, 25), 
     xlim = xlim_range, main = "East shore")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_GB_p$date, df_GB_p$middle_ER, pch = 1, col = "#a67d17")
abline(h = 0, col = "black", lwd = 1)
mtext( expression(Metabolism~(mmol~O[2]~m^-3~d^-1)), side = 2, line = 1.85, col = "black")
points(df_SH_p$date, df_SH_p$middle_GPP, pch = 17, col = "#c86640")
points(df_SH_p$date, df_SH_p$middle_ER, pch = 2, col = "#c86640")
# 
# arrows(x0 = df_GB_p$date,
#        y0 = df_GB_p$lower_GPP,
#        x1 = df_GB_p$date,
#        y1 = df_GB_p$upper_GPP,
#        angle = 90, code = 2, length = 0.05, col = "#a67d17")



# GAM smooths
library(mgcv)
gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_GB_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SH_p)
date_seq <- seq(min(df_GB_p$date), max(df_GB_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#a67d17", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#c86640", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#a67d17", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#c86640", alpha.f = 0.2), border = NA)


gam_gb_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_GB_p)
gam_sh_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_SH_p)
date_seq_e <- seq(min(df_GB_p$date), max(df_GB_p$date), by = "1 day")
pred_gb_e <- predict(gam_gb_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
pred_sh_e <- predict(gam_sh_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
lines(date_seq_e, pred_gb_e$fit, col = "#a67d17", lwd = 2)
lines(date_seq_e, pred_sh_e$fit, col = "#c86640", lwd = 2)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_gb_e$fit + 2*pred_gb_e$se.fit, rev(pred_gb_e$fit - 2*pred_gb_e$se.fit)),
        col = adjustcolor("#a67d17", alpha.f = 0.2), border = NA)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_sh_e$fit + 2*pred_sh_e$se.fit, rev(pred_sh_e$fit - 2*pred_sh_e$se.fit)),
        col = adjustcolor("#c86640", alpha.f = 0.2), border = NA)


# Flow and PPT on right
par(new = TRUE)
flow_ylim <- rev(range(df_GB_p$flow_mean, na.rm = TRUE) + c(0, 1.5 * diff(range(df_GB_p$flow_mean, na.rm = TRUE))))
plot(df_GB_p$date, df_GB_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")


par(new = TRUE)
ppt_max <- max(df_GB_p$ppt_mm, na.rm = TRUE)
ppt_ylim <- rev(c(0, ppt_max * 2.85))

plot(df_GB_p$date, df_GB_p$ppt_mm, type = "n", axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)

# Draw vertical bars for precipitation
segments(x0 = df_GB_p$date,
         y0 = 0,
         x1 = df_GB_p$date,
         y1 = df_GB_p$ppt_mm,
         col = "#14c7bb", lwd = 3)

# Right-hand axis
axis(4,
     at = pretty(ppt_ylim),
     labels = pretty(ppt_ylim),
     line = 3.75, col.axis = "#14c7bb", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 6, col = "#14c7bb")

# legend("bottom", inset = c(-0.05, -0.05), xpd = TRUE,
#        legend = c("Small inflow", "No inflow", "Streamflow", "Precipitation"), 
#        col = c("#a67d17", "#c86640", "#448ff2", "#6fded7"), 
#        pch = c(16, 17, NA, NA), 
#        lwd = c(NA, NA, 3, 3), 
#        lty = c(NA, NA, 3, 1),
#        y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)

# === SECOND PLOT (West shore) ===

plot(df_BW_p$date, df_BW_p$middle_GPP, type = "p", pch = 16, col = "#3283a8",
     xaxt = "n", xlab = "", ylab = "",
      ylim = c(-30, 35), xlim = xlim_range, main = "West shore")
axis(1, at = tick_dates, labels = format(tick_dates, "%d-%b"), las = 1, cex.axis = 0.8)
points(df_BW_p$date, df_BW_p$middle_ER, pch = 1, col = "#3283a8")
abline(h = 0, col = "black", lwd = 1)
points(df_SS_p$date, df_SS_p$middle_GPP, pch = 17, col = "#136F63")
points(df_SS_p$date, df_SS_p$middle_ER, pch = 2, col = "#136F63")
abline(h = 0, col = "black", lwd = 1)
mtext( expression(Metabolism~(mmol~O[2]~m^-3~d^-1)), side = 2, line = 1.85, col = "black")



gam_gb <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_BW_p)
gam_sh <- gam(middle_GPP ~ s(as.numeric(date), k = 10), data = df_SS_p)
date_seq <- seq(min(df_BW_p$date), max(df_BW_p$date), by = "1 day")
pred_gb <- predict(gam_gb, newdata = data.frame(date = date_seq), se.fit = TRUE)
pred_sh <- predict(gam_sh, newdata = data.frame(date = date_seq), se.fit = TRUE)
lines(date_seq, pred_gb$fit, col = "#3283a8", lwd = 2)
lines(date_seq, pred_sh$fit, col = "#136F63", lwd = 2)
polygon(c(date_seq, rev(date_seq)), c(pred_gb$fit + 2*pred_gb$se.fit, rev(pred_gb$fit - 2*pred_gb$se.fit)),
        col = adjustcolor("#3283a8", alpha.f = 0.2), border = NA)
polygon(c(date_seq, rev(date_seq)), c(pred_sh$fit + 2*pred_sh$se.fit, rev(pred_sh$fit - 2*pred_sh$se.fit)),
        col = adjustcolor("#136F63", alpha.f = 0.2), border = NA)




gam_gb_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_BW_p)
gam_sh_e <- gam(middle_ER ~ s(as.numeric(date), k = 10), data = df_SS_p)
date_seq_e <- seq(min(df_BW_p$date), max(df_BW_p$date), by = "1 day")
pred_gb_e <- predict(gam_gb_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
pred_sh_e <- predict(gam_sh_e, newdata = data.frame(date = date_seq_e), se.fit = TRUE)
lines(date_seq, pred_gb_e$fit, col = "#3283a8", lwd = 2)
lines(date_seq, pred_sh_e$fit, col = "#136F63", lwd = 2)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_gb_e$fit + 2*pred_gb_e$se.fit, rev(pred_gb_e$fit - 2*pred_gb_e$se.fit)),
        col = adjustcolor("#3283a8", alpha.f = 0.2), border = NA)
polygon(c(date_seq_e, rev(date_seq_e)), c(pred_sh_e$fit + 2*pred_sh_e$se.fit, rev(pred_sh_e$fit - 2*pred_sh_e$se.fit)),
        col = adjustcolor("#136F63", alpha.f = 0.2), border = NA)

par(new = TRUE)
flow_ylim <- rev(range(df_BW_p$flow_mean, na.rm = TRUE) + c(0, 1.5 * diff(range(df_BW_p$flow_mean, na.rm = TRUE))))
plot(df_BW_p$date, df_BW_p$flow_mean, type = "l", col = "#448ff2", lwd = 3, lty=3,
     axes = FALSE, xlab = "", ylab = "", ylim = flow_ylim)
axis(4, col.axis = "#448ff2", col = "black")
mtext(expression("Streamflow ("*m^3*~s^{-1}*")"), side = 4, line = 2.5, col = "#448ff2")


par(new = TRUE)
ppt_max <- max(df_BW_p$ppt_mm, na.rm = TRUE)
ppt_ylim <- rev(c(0, ppt_max * 2.85))

plot(df_BW_p$date, df_BW_p$ppt_mm, type = "n", axes = FALSE, xlab = "", ylab = "", ylim = ppt_ylim)

# Draw vertical bars for precipitation
segments(x0 = df_BW_p$date,
         y0 = 0,
         x1 = df_BW_p$date,
         y1 = df_BW_p$ppt_mm,
         col = "#14c7bb", lwd = 3)

# Right-hand axis
axis(4,
     at = pretty(ppt_ylim),
     labels = pretty(ppt_ylim),
     line = 3.75, col.axis = "#14c7bb", col = "black")
mtext(expression("Precipitation (mm)"), side = 4, line = 6, col = "#14c7bb")


# legend("bottom", inset = c(-0.05, -0.05), xpd = TRUE,
#        legend = c("Large inflow", "No inflow", "Streamflow", "Precipitation"), 
#        col = c("#3283a8", "#136F63", "#448ff2", "#6fded7"), 
#        pch = c(16, 17, NA, NA), 
#        lwd = c(NA, NA, 3, 3), 
#        lty = c(NA, NA, 3, 1),
#        y.intersp = 1.2, x.intersp = 0.15, bty = "n", horiz = TRUE, cex = 0.9)


#
#dev.off()
```





### Paired differences between shores near and away from streams 

(weekly averaged data)

```{r, warning=F, size = 'small', echo=F, include=FALSE}
# 
# df_BW_p <- pdat %>%
#   filter(shore == "BW") %>%
#   filter(year==2023) %>%
#   filter(week>1 & week<41) %>%
#   dplyr::group_by(shore, week, WaterYear) %>%
#   dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")
# 
# 
# df_SS_p <- pdat %>%
#   filter(shore == "SS") %>%
#   filter(year==2023) %>%
#   filter(week>1 & week<41)%>%
#   dplyr::group_by(shore, week, WaterYear) %>%
#   dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

df_west_subset <- rbind(df_BW_p, df_SS_p)%>%
  dplyr::select(shore, date, week, middle_GPP, middle_ER_ab, lake_tempC, lake_SPC, ppt_mm, 
                light_mean, windsp_mean, OM,
                NO3_mgL_dl, NH4_mgL_dl, PO4_ugL_dl, DOC_mgL_dl)



df_west_subset2 <- rbind(df_BW_p, df_SS_p)%>%
  dplyr::select(shore, date, middle_GPP, middle_ER_ab, light_mean, lake_tempC, lake_SPC)

df_wide_w <- df_west_subset2 %>%
  pivot_wider(
    id_cols = date,
    names_from = shore,
    values_from = c(middle_GPP, middle_ER_ab, light_mean, lake_tempC, lake_SPC),  # use your actual variable names here
    names_glue = "{.value}_{shore}"
  )


df_diff_w <- df_wide_w %>%
  mutate(across(ends_with("_BW"), 
                ~ . - get(sub("_BW", "_SS", cur_column())),
                .names = "diff_{.col}"))


df_only_diffs_w <- df_diff_w %>%
  select(date, starts_with("diff_"))
  
df_long_west <- df_only_diffs_w %>%
  pivot_longer(
    cols = -date,
    names_to = "variable",
    values_to = "difference"
  )

# 
# 
# coef_order <- c(
#   "diff_middle_GPP_BW",
#   "diff_middle_ER_ab_BW",
#   "diff_lake_tempC_BW",
#   "diff_lake_SPC_BW",
#   "diff_light_mean_BW",
#   "diff_light_mean_BW",
#   "diff_windsp_mean_BW",
#   "diff_OM_BW",
#   "diff_NO3_mgL_dl_BW",
#   "diff_NH4_mgL_dl_BW", 
#   "diff_PO4_ugL_dl_BW",
#   "diff_DOC_mgL_dl_BW"
#   
# )
# 
# df_long_west <- df_long_west %>%
#   mutate(variable = fct_relevel(variable, rev(coef_order)))

var_labs <- c(
  "diff_middle_GPP_BW" = "GPP", 
  "diff_middle_ER_ab_BW" = "ER", 
  "diff_lake_tempC_BW" = "W.Temp.", 
  "diff_lake_SPC_BW" = "SPC",
  "diff_light_mean_BW" = "Light",
  "diff_windsp_mean_BW" = "Wind",
    "diff_ppt_mm_BW" = "PPT",
  "diff_OM_BW" = "OM",
  "diff_NO3_mgL_dl_BW" = "NO[3]^'-'",
  "diff_NH4_mgL_dl_BW" = "NH[4]^'+'",
  "diff_PO4_ugL_dl_BW" = "Ophos",
  "diff_DOC_mgL_dl_BW" = "DOC")



df_long_west2 <- df_long_west %>%
  mutate(variable = sub("_BW$", "", variable))

df_long_west2$shore <- "BW"


```





```{r, warning=F, echo=FALSE, include=F, fig.width=8, fig.height=6}

west_shore_diff <- ggplot(df_long_west, aes(x = date, y = difference)) +
  geom_point(color = "steelblue", shape=19) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~ variable, scales = "free_y", ncol = 4,
             labeller = labeller(variable = as_labeller(var_labs, label_parsed))) +
  theme_minimal(base_size = 12) +
  labs(title = "Habitat differences (BW - SS)",
       x = "Week",
       y = "Difference") +
  theme(strip.text = element_text(size = 10, face = "bold")) +
    scale_x_date(
  date_breaks = "4 week",
  date_labels = "%d-%b"
  #limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))
  )

west_shore_diff
```

### Paired shore analysis:

Reporting the % differences for all water quality in the MS text.   
Just GPP and ER can be added at the time series.

We are interested in GPP diff shapes for west for east - for all the combinations to get the difference 
Light and temp on x and GPP on y 

Way of are the inflow sites more similar to each other or GPP and light - verse ER- with temp 
Nearshore locations regardless of shore are more similar to each than location -  or they aren't 


```{r, warning=F, size = 'small', echo=F, include=FALSE}

# df_GB_p <- pdat %>%
#   filter(shore == "GB") %>%
#   filter(year==2023) %>%
#   filter(week>4 & week<41) %>%
#   dplyr::group_by(shore, week, WaterYear) %>%
#   dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")
# 
# df_SH_p <- pdat %>%
#   filter(shore == "SH") %>%
#   filter(year==2023) %>%
#   filter(week>4 & week<41)%>%
#   dplyr::group_by(shore, week, WaterYear) %>%
#   dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

df_east_subset <- rbind(df_GB_p, df_SH_p)%>%
  dplyr::select(shore, week, middle_GPP, middle_ER_ab, lake_tempC, lake_SPC, ppt_mm, 
                light_mean, windsp_mean, OM,
                NO3_mgL_dl, NH4_mgL_dl, PO4_ugL_dl, DOC_mgL_dl)


df_west_subset2 <- rbind(df_GB_p, df_SH_p)%>%
  dplyr::select(shore, date, middle_GPP, middle_ER_ab, light_mean, lake_tempC, lake_SPC)


df_wide_e <- df_west_subset2 %>%
  pivot_wider(
    id_cols = date,
    names_from = shore,
    values_from = c(middle_GPP, middle_ER_ab, light_mean, lake_tempC, lake_SPC),  # use your actual variable names here
    names_glue = "{.value}_{shore}"
  )


df_diff_e <- df_wide_e %>%
  mutate(across(ends_with("_GB"), 
                ~ . - get(sub("_GB", "_SH", cur_column())),
                .names = "diff_{.col}"))


df_only_diffs_e <- df_diff_e %>%
  select(date, starts_with("diff_"))
  
df_long_east <- df_only_diffs_e %>%
  pivot_longer(
    cols = -date,
    names_to = "variable",
    values_to = "difference"
  )

var_labs <- c(
  "diff_middle_GPP_GB" = "GPP", 
  "diff_middle_ER_ab_GB" = "ER", 
  "diff_lake_tempC_GB" = "W.Temp.", 
  "diff_lake_SPC_GB" = "SPC",
  "diff_light_mean_GB" = "Light",
  "diff_windsp_mean_GB" = "Wind",
    "diff_ppt_mm_GB" = "PPT",
  "diff_OM_GB" = "OM",
  "diff_NO3_mgL_dl_GB" = "NO[3]^'-'",
  "diff_NH4_mgL_dl_GB" = "NH[4]^'+'",
  "diff_PO4_ugL_dl_GB" = "Ophos",
  "diff_DOC_mgL_dl_GB" = "DOC")



var_labs <- c(
  "diff_middle_GPP" = "GPP", 
  "diff_middle_ER_ab" = "ER", 
  "diff_lake_tempC" = "W.Temp.", 
  "diff_lake_SPC" = "SPC")


df_long_east2 <- df_long_east %>%
  mutate(variable = sub("_GB$", "", variable))

df_long_east2$shore <- "GB"

```

```{r, warning=F, echo=FALSE, include=T, fig.width=9.5, fig.height=7}

long_df <- rbind(df_long_east2, df_long_west2)

long_df <- long_df %>%
  mutate(variable = factor(variable, levels = c(
    "diff_middle_GPP", 
    "diff_middle_ER_ab", 
    "diff_light_mean", 
    "diff_lake_tempC",
    "diff_lake_SPC"
    
  )))

var_labs <- c(
  "diff_middle_GPP" = "GPP",
  "diff_middle_ER_ab" = "ER",
  "diff_light_mean" = "Light",
    "diff_lake_tempC" = "Temperature",
        "diff_lake_SPC" = "SPC"
  
)

shore_diff <- ggplot(long_df, aes(x = date, y = (difference), color = shore, shape = shore)) +
  geom_point(alpha = 0.75, size=2.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~ variable, ncol = 2, nrow = 3,
             labeller = labeller(variable = as_labeller(var_labs, label_parsed)), scale="free") +
  theme_classic(base_size = 12) +
  scale_x_date(
    date_breaks = "6 week",
    date_labels = "%d-%b"
  ) +
  labs(
    x = NULL,
    y = expression(Scaled~Delta)
  ) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    name = "Shore",
    values = c(BW = "#3283a8", GB = "#a67d17"),
    labels = c(BW = "West shore", GB = "East shore")
  ) +
  scale_shape_manual(
    name = "Shore",
    values = c(BW = 19, GB = 17),
    labels = c(BW = "West shore", GB = "East shore")
  )

shore_diff


shore_diff_sum <- long_df %>%
  group_by(variable, shore) %>%
  summarise(
    diff_m = mean(difference, na.rm = TRUE),
    diff_sd = sd(difference, na.rm = TRUE),
    n = sum(!is.na(difference)),
    diff_se = diff_sd / sqrt(n),
    .groups = "drop"
  )


```

```{r, warning=F, size = 'small', echo=F, include=FALSE}
# ggsave("/Users/kellyloria/Documents/Publications/CH2\ Streamflow\ and\ nearshore\ metabolism/LandO_Submission/Revisions/Figures/Fig_nearshore_dat_shore_diff_lg.png", plot = shore_diff, width = 7, height = 7, units = "in")

```



```{r, warning=F, echo=FALSE, include=F}

date_seq <- seq(from = as.Date("2021-06-01"), to = as.Date("2023-09-20"), by = "day")
date_df <- data.frame(date = date_seq)
date_df <- date_df %>%
  mutate(yday=yday(date),
         year = year(date))


library(dplyr)
library(lubridate)

water_year_week <- function(data) {
  data %>%
    mutate(date = ymd(date)) %>%
    mutate(
      WaterYear = if_else(month(date) >= 10, year(date) + 1, year(date)),
      wy_start = ymd(paste0(WaterYear - 1, "-10-01")),
      WY_week = as.integer(floor(difftime(date, wy_start, units = "weeks")) + 1)
    ) %>%
    select(-wy_start)  # optional, to clean up intermediate column
}


date_df <- water_year_week(date_df)

week_df <- date_df %>%
  dplyr::select(WaterYear, WY_week)


```


```{r, warning=F, echo=FALSE, include=F, fig.width=5, fig.height=4}

dat <- water_year_week(dat)

# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_BW <- dat %>%
  mutate(middle_ER_ab = c(middle_ER*-1)) %>%
  dplyr::select(shore, date, WY_week, WaterYear, 
                lake_DO, middle_GPP, middle_ER_ab, middle_NEP,
                lake_tempC, ppt_mm, light_mean) %>%
  filter(shore == "BW") %>%
  dplyr::group_by(shore, WY_week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

summary(GPP_df_BW)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO_BW <- GPP_df_BW %>%
    filter(!is.na(lake_DO)) %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         plot_ER = ifelse(is.na(middle_ER_ab), 0, middle_ER_ab), 
         plot_NEP = ifelse(is.na(middle_NEP), 0, middle_NEP))

# Identify the unique yday values for each year
week_2022 <- unique(plot_data_DO_BW$WY_week[plot_data_DO_BW$WaterYear == 2022])
week_2023 <- unique(plot_data_DO_BW$WY_week[plot_data_DO_BW$WaterYear == 2023])

# Find the common yday values across all three years
common_week_BW <- Reduce(intersect, list(week_2022, 
                                      week_2023))

# Filter the dataframe for only those common yday values
filtered_data_BW <- plot_data_DO_BW %>%
  filter(WY_week %in% common_week_BW & WaterYear %in% c(2022, 2023))

filtered_data_BW_cs <- filtered_data_BW%>%
  arrange(WY_week, WaterYear) %>%
  group_by(WaterYear) %>%
  mutate(GPPcumsum = cumsum(plot_GPP),
         ERcumsum = cumsum(plot_ER), 
         NEPcumsum = cumsum(plot_NEP))


filtered_data_BW_csT<- filtered_data_BW_cs%>%filter(WaterYear==2022)

filtered_data_BW_csT1<- filtered_data_BW_cs%>%filter(WaterYear==2023)


BW_week_df <- week_df %>%
  left_join(filtered_data_BW, by=c("WY_week", "WaterYear"))


BW_plot <- ggplot(filtered_data_BW_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = GPPcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
  labs(x = "Week of Water Year", color = "Year", 
       title = "BW: west shore large inflow") +
      ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +    ylim(0,335) +
  scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 

BW_plot


BW_plot_ER <- ggplot(filtered_data_BW_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = ERcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
  labs(x = "Week of Water Year", color = "Year") +
            ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +   # ylim(0,335) +    
  ylim(0,410) +
    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 
  theme_classic() 

BW_plot_ER





BW_plot_NEP <- ggplot(filtered_data_BW_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = plot_NEP, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
  labs(x = "Week of Water Year", color = "Year") +
            ylab(expression(NEP~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +   # ylim(0,335) +    
  #ylim(0,400) +
    ylim(-12, 12) +
       geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 

BW_plot_NEP
# # Compute the maximum cumulative GPP for each year
# date_datf_plt_sum <- date_datf_plt_bw %>%
#   group_by(year) %>%
#   summarise(
#     T_gpp = max(GPP_cumsum, na.rm = TRUE)) %>%
#   mutate(percent_change = (T_gpp -T_gpp[year == 2023]) / T_gpp * 100)


```



```{r, warning=F, echo=FALSE, include=F, fig.width=5, fig.height=4}

dat <- water_year_week(dat)

# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_GB <- dat %>%
  mutate(middle_ER_ab = c(middle_ER*-1)) %>%
  dplyr::select(shore, date, WY_week, WaterYear, lake_DO, middle_GPP, middle_ER_ab, 
                middle_NEP, 
                lake_tempC, ppt_mm, light_mean) %>%
  filter(shore == "GB") %>%
  dplyr::group_by(shore, WY_week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

summary(GPP_df_GB)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO_GB <- GPP_df_GB %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         plot_ER = ifelse(is.na(middle_ER_ab), 0, middle_ER_ab),
                  plot_NEP = ifelse(is.na(middle_NEP), 0, middle_NEP))


# Identify the unique yday values for each year
week_2022 <- unique(plot_data_DO_GB$WY_week[plot_data_DO_GB$WaterYear == 2022])
week_2023 <- unique(plot_data_DO_GB$WY_week[plot_data_DO_GB$WaterYear == 2023])

# Find the common yday values across all three years
common_week_GB <- Reduce(intersect, list(week_2022, 
                                      week_2023))

# Filter the dataframe for only those common yday values
filtered_data_GB <- plot_data_DO_GB %>%
  filter(WY_week %in% common_week_GB & WaterYear %in% c(2022, 2023))

filtered_data_GB_cs <- filtered_data_GB%>%
  arrange(WY_week, WaterYear) %>%
  group_by(WaterYear) %>%
  mutate(GPPcumsum = cumsum(plot_GPP),
         ERcumsum = cumsum(plot_ER))


filtered_data_GB_csT<- filtered_data_GB_cs%>%filter(WaterYear==2022)

filtered_data_GB_csT1<- filtered_data_GB_cs%>%filter(WaterYear==2023)


GB_week_df <- week_df %>%
  left_join(filtered_data_GB, by=c("WY_week", "WaterYear"))


GB_plot <- ggplot(filtered_data_GB_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = GPPcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year", 
         title = "GB: east shore small inflow") +
     # ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +
      ylab(NULL) +
      ylim(0,335) +
    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 

GB_plot



GB_plot_ER <- ggplot(filtered_data_GB_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = ERcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
      #    ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
xlab(NULL) +
      ylab(NULL) +
      ylim(0,410) +
  scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 



GB_plot_NEP <- ggplot(filtered_data_GB_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = plot_NEP, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
      #    ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
xlab(NULL) +
      ylab(NULL) +
    ylim(-12, 12) +
   #   ylim(0,410) +
    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
         geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
  theme_classic() 


# # Compute the maximum cumulative GPP for each year
# date_datf_plt_sum <- date_datf_plt_bw %>%
#   group_by(year) %>%
#   summarise(
#     T_gpp = max(GPP_cumsum, na.rm = TRUE)) %>%
#   mutate(percent_change = (T_gpp -T_gpp[year == 2023]) / T_gpp * 100)


```




```{r, warning=F, echo=FALSE, include=F, fig.width=5, fig.height=4}

dat <- water_year_week(dat)

# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_SS <- dat %>%
  mutate(middle_ER_ab = c(middle_ER*-1)) %>%
  dplyr::select(shore, date, WY_week, WaterYear, lake_DO, middle_GPP, middle_ER_ab, 
                middle_NEP,
                lake_tempC, ppt_mm, light_mean) %>%
  filter(shore == "SS") %>%
  dplyr::group_by(shore, WY_week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

summary(GPP_df_SS)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO_SS <- GPP_df_SS %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         plot_ER = ifelse(is.na(middle_ER_ab), 0, middle_ER_ab),
                  plot_NEP = ifelse(is.na(middle_NEP), 0, middle_NEP)
         )

# Identify the unique yday values for each year
week_2022 <- unique(plot_data_DO_SS$WY_week[plot_data_DO_SS$WaterYear == 2022])
week_2023 <- unique(plot_data_DO_SS$WY_week[plot_data_DO_SS$WaterYear == 2023])

# Find the common yday values across all three years
common_week_SS <- Reduce(intersect, list(week_2022, 
                                      week_2023))

# Filter the dataframe for only those common yday values
filtered_data_SS <- plot_data_DO_SS %>%
  filter(WY_week %in% common_week_SS & WaterYear %in% c(2022, 2023))

filtered_data_SS_cs <- filtered_data_SS%>%
  arrange(WY_week, WaterYear) %>%
  group_by(WaterYear) %>%
  mutate(GPPcumsum = cumsum(plot_GPP),
         ERcumsum = cumsum(plot_ER))


filtered_data_SS_csT<- filtered_data_SS_cs%>%filter(WaterYear==2022)

filtered_data_SS_csT1<- filtered_data_SS_cs%>%filter(WaterYear==2023)


SS_week_df <- week_df %>%
  left_join(filtered_data_SS, by=c("WY_week", "WaterYear"))


SS_plot <- ggplot(filtered_data_SS_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = GPPcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year", 
         title = "SS: west shore no inflow") +
   #   ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +
      ylab(NULL) +
  ylim(0,335) +
    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)"))+  theme_classic() 

SS_plot



SS_plot_E <- ggplot(filtered_data_SS_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = ERcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
     #   ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
xlab(NULL) +
      ylab(NULL) +
      ylim(0,410) +    scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)")) +
  theme_classic() 

SS_plot_E




SS_plot_NEP <- ggplot(filtered_data_SS_cs%>%filter(WaterYear>2021), aes(x = WY_week, y = plot_NEP, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
     #   ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
xlab(NULL) +     geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +

      ylab(NULL) +
    ylim(-12, 12) +
  #    ylim(0,410) +     
  scale_color_manual(values=c("#c94738", "#054fb9"), name= "WY", 
                     labels = c("2022 (dry)", "2023 (wet)"))+
  theme_classic() 

SS_plot_NEP

# # Compute the maximum cumulative GPP for each year
# date_datf_plt_sum <- date_datf_plt_bw %>%
#   group_by(year) %>%
#   summarise(
#     T_gpp = max(GPP_cumsum, na.rm = TRUE)) %>%
#   mutate(percent_change = (T_gpp -T_gpp[year == 2023]) / T_gpp * 100)


```




```{r, warning=F, echo=FALSE, include=F, fig.width=5, fig.height=4}

dat <- water_year_week(dat)

# Filter the dataset to only include rows where do.obs_m or GPP_mean are not NA
GPP_df_SH <- dat %>%
  mutate(middle_ER_ab = c(middle_ER*-1)) %>%
  dplyr::select(shore, date, WY_week, WaterYear, lake_DO, middle_GPP, middle_ER_ab, 
                middle_NEP,
                lake_tempC, ppt_mm, light_mean) %>%
  filter(shore == "SH") %>%
  dplyr::group_by(shore, WY_week, WaterYear) %>%
  dplyr::summarise(across(everything(), mean, na.rm = TRUE), .groups = "drop")

summary(GPP_df_SH)
# date range 2021-06-11  to 2023-09-14   

plot_data_DO_SH <- GPP_df_SH %>%
  mutate(has_do = !is.na(lake_DO), 
         has_GPP = !is.na(middle_GPP),
         plot_GPP = ifelse(is.na(middle_GPP), 0, middle_GPP),
         has_ER = !is.na(middle_ER_ab),
         plot_ER = ifelse(is.na(middle_ER_ab), 0, middle_ER_ab),
         plot_NEP = ifelse(is.na(middle_NEP), 0, middle_NEP))

# Identify the unique yday values for each year
week_2022 <- unique(plot_data_DO_SH$WY_week[plot_data_DO_SH$WaterYear == 2022])
week_2023 <- unique(plot_data_DO_SH$WY_week[plot_data_DO_SH$WaterYear == 2023])

# Find the common yday values across all three years
common_week_SH <- Reduce(intersect, list(week_2022, 
                                      week_2023))

# Filter the dataframe for only those common yday values
filtered_data_SH <- plot_data_DO_SH %>%
  filter(WY_week %in% common_week_SH & WaterYear %in% c(2023))

filtered_data_SH_cs <- filtered_data_SH%>%
  arrange(WY_week, WaterYear) %>%
  group_by(WaterYear) %>%
  mutate(GPPcumsum = cumsum(plot_GPP),
         ERcumsum = cumsum(plot_ER)
           )


filtered_data_SH_csT<- filtered_data_SH_cs%>%filter(WaterYear==2022)

filtered_data_SH_csT1<- filtered_data_SH_cs%>%filter(WaterYear==2023)


SH_week_df <- week_df %>%
  left_join(filtered_data_SH, by=c("WY_week", "WaterYear"))


SH_plot <- ggplot(filtered_data_SH_cs%>%filter(WaterYear>2022), aes(x = WY_week, y = GPPcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year", 
         title = "SH: east shore no inflow") +
     # ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +
      ylab(NULL) +
    ylim(0,335) +
      scale_color_manual(values=c("#054fb9"), name= "WY", 
                     labels = c("2023 (wet)")) +
  theme_classic() 

SH_plot



SH_plot_E <- ggplot(filtered_data_SH_cs%>%filter(WaterYear>2022), aes(x = WY_week, y = ERcumsum, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
     # ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +
    ylab(NULL) +
    ylim(0,410) +
      scale_color_manual(values=c("#054fb9"), name= "WY", 
                     labels = c("2023 (wet)")) +  theme_classic() 

SH_plot_NEP <- ggplot(filtered_data_SH_cs%>%filter(WaterYear>2022) %>%filter(WY_week> 18) %>%  mutate(middle_NEP = ifelse(is.na(middle_NEP), 0, middle_NEP)), aes(x = WY_week, y = middle_NEP, color = factor(WaterYear))) +
  geom_line(size = 1, alpha=0.95) + 
    labs(x = "Week of Water Year", color = "Year") +
     # ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1)))+
  xlab(NULL) +
    ylab(NULL) +
  xlim(0,51)+
  ylim(-12, 12) +
       geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
    #ylim(0,410) +
      scale_color_manual(values=c("#054fb9"), name= "WY", 
                     labels = c("2023 (wet)")) +
  theme_classic() 

SH_plot_NEP
# # Compute the maximum cumulative GPP for each year
# date_datf_plt_sum <- date_datf_plt_bw %>%
#   group_by(year) %>%
#   summarise(
#     T_gpp = max(GPP_cumsum, na.rm = TRUE)) %>%
#   mutate(percent_change = (T_gpp -T_gpp[year == 2023]) / T_gpp * 100)


```

### Cummulative GPP and ER in wet and dry years 
 
 weekly dynamics

```{r, warning=F, echo=FALSE, include=T, fig.width=12, fig.height=6}

Cumsum_grid <- ggarrange(
  BW_plot,
  SS_plot,
  GB_plot,
  SH_plot,
  BW_plot_ER,
  SS_plot_E,
  GB_plot_ER,
  SH_plot_E,
  BW_plot_NEP,
  SS_plot_NEP,
  GB_plot_NEP,
  SH_plot_NEP,
  align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
  #hjust = 0.1,
  vjust = 1,
    common.legend = TRUE, 
  legend = "bottom",
 ncol = 4, nrow = 3)

Cumsum_grid

```




```{r, warning=F, size = 'small', echo=F, include=F, fig.width=6, fig.height=4}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/SI_gppCS_panel_long.png", plot = Cumsum_grid, width = 12, height = 6, units = "in")

```



### NEP in wet and dry years 


```{r, warning=F, echo=FALSE, include=F, fig.width=12, fig.height=2}

Cumsum_grid <- ggarrange(
  BW_plot_NEP,
  SS_plot_NEP,
  GB_plot_NEP,
  SH_plot_NEP,
  align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
  #hjust = 0.1,
  vjust = 1,
    common.legend = TRUE, 
  legend = "bottom",
 ncol = 4, nrow = 1)

Cumsum_grid

```

#### Other important metabolic relationships: 

- ER and GPP 

- GPP and light

- ER and Temp


Overlapping weekly metabolism, light, and temperature from WY 22 and WY 23 for all shores

```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}
week_dat_all_shore <- rbind(
  filtered_data_BW_cs,
  filtered_data_GB_cs,
  filtered_data_SS_cs,
  filtered_data_SH_cs)


library(dplyr)
library(broom)

# Compute correlation coefficients and p-values per shore
cor_stats <- week_dat_all_shore %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(light_mean), log10(middle_GPP), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
  mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))

# Merge with max x/y position per shore to position text nicely
label_positions <- week_dat_all_shore %>%
  group_by(shore) %>%
  summarise(
    x = 240,
    y = 1.5
  ) %>%
  left_join(cor_stats, by = "shore")

# Now the plot
GPP_light_plots <- ggplot(week_dat_all_shore, aes(y = middle_GPP, x = light_mean, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.75) +
  scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  ylab(expression(log(GPP)~(mmol~O[2]~m^-3~d^-1))) +
  xlab(expression(log(Benthic~light)~(mu*mol~m^-2~s^-1))) +
  geom_smooth(method="lm", se=F) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
    labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
               SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
    labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
               SS = "West shore no inflow", SH = "East shore no inflow")) +
  geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
  theme_classic() +
  facet_grid(shore ~ .)

GPP_light_plots


```



```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}

# Compute correlation coefficients and p-values per shore
cor_stats <- week_dat_all_shore %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(lake_tempC), log10(middle_ER_ab), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
    mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))

# Merge with max x/y position per shore to position text nicely
label_positions <- week_dat_all_shore %>%
  group_by(shore) %>%
  summarise(
    x = max((lake_tempC), na.rm = TRUE),
    y = 22
  ) %>%
  left_join(cor_stats, by = "shore")



ER_temp_plots <- ggplot(week_dat_all_shore, aes(y = middle_ER_ab, x = lake_tempC, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.75) +
    scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
      scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
    xlab(expression(log(Benthic~temperature)~(degree*C))) +
    ylab(expression(log("|"~ER~"|")~(mmol~O[2]~m^-3~d^-1))) +
 geom_smooth(method="lm", se=F) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
        labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
       labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  theme_classic()  +
    geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
      facet_grid(shore~.) 

ER_temp_plots

```


```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}



# Compute correlation coefficients and p-values per shore
cor_stats <- week_dat_all_shore %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(middle_GPP), log10(middle_ER_ab), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
      mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))


# Merge with max x/y position per shore to position text nicely
label_positions <- week_dat_all_shore %>%
 group_by(shore) %>%
  summarise(
    x = 15,
    y = 22
  ) %>%
  left_join(cor_stats, by = "shore")



GPP_ER_plots <- ggplot(week_dat_all_shore, aes(y = middle_ER_ab, x = middle_GPP, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.75) +
      scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
    scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  xlab(expression(log(GPP)~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression(log("|"~ER~"|")~(mmol~O[2]~m^-3~d^-1))) +
  geom_smooth(method="lm", se=F) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
        labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
       labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  theme_classic() +
    geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
      facet_grid(shore~.)


GPP_ER_plots

```


```{r, warning=F, echo=FALSE, include=T, fig.width=8, fig.height=8}

metab_grid <- ggarrange(
  GPP_ER_plots,
  GPP_light_plots,
  ER_temp_plots,
  align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
  #hjust = 0.1,
  vjust = 1,
    common.legend = TRUE, 
  legend = "bottom",
 ncol = 3, nrow = 1)

metab_grid

```

#### Daily data:

Only on shared observations witin shore for GPP and ER from WY 22 and WY 23

```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}

day_dat_all_shore <- rbind(
  filtered_data_BW_d,
  filtered_data_GB_d,
  filtered_data_SS_d,
  filtered_data_SH_d)
```


```{r, warning=F, echo=FALSE, include=F, fig.width=6, fig.height=12}


library(dplyr)
library(broom)

# Compute correlation coefficients and p-values per shore
cor_stats <- day_dat_all_shore %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(light_mean), log10(middle_GPP), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
  mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))

# Merge with max x/y position per shore to position text nicely
label_positions <- day_dat_all_shore %>%
  group_by(shore) %>%
  summarise(
    x = 250,
    y = 0.15
  ) %>%
  left_join(cor_stats, by = "shore")

# Now the plot
GPP_light_plots <- ggplot(day_dat_all_shore, aes(y = middle_GPP, x = light_mean, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.35) +
  scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  ylab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  xlab(expression(Benthic~light~(mu*mol~m^-2~s^-1))) +
    geom_smooth(
    data = subset(day_dat_all_shore, shore != "SS"),
    method = "lm", se = FALSE
  ) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
    labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
               SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
    labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
               SS = "West shore no inflow", SH = "East shore no inflow")) +
  geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
  theme_classic() +
  facet_grid(shore ~ .)

GPP_light_plots


```



```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}

# Compute correlation coefficients and p-values per shore
cor_stats <- day_dat_all_shore %>%
  filter(middle_ER_ab<40) %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(lake_tempC), log10(middle_ER_ab), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
    mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))

# Merge with max x/y position per shore to position text nicely
label_positions <- day_dat_all_shore %>%
  filter(middle_ER_ab<40) %>%
  group_by(shore) %>%
  summarise(
    x = 19,
    y = 36
  ) %>%
  left_join(cor_stats, by = "shore")



ER_temp_plots <- ggplot(day_dat_all_shore%>%filter(middle_ER_ab<40), aes(y = middle_ER_ab, x = lake_tempC, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.35) +
    scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
      scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
    xlab(expression(Water~temperature~(degree*C))) +
    ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1))) +
      geom_smooth(
    data = subset(day_dat_all_shore, shore != "BW"),
    method = "lm", se = FALSE
  ) +
 
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
        labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
       labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  theme_classic()  +
    geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
      facet_grid(shore~.) 

ER_temp_plots

```




```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}



# Compute correlation coefficients and p-values per shore
cor_stats <- day_dat_all_shore %>%
  group_by(shore) %>%
  summarise(cor_test = list(cor.test(log10(middle_GPP), log10(middle_ER_ab), method = "pearson"))) %>%
  mutate(tidy = purrr::map(cor_test, broom::tidy)) %>%
  unnest(tidy) %>%
      mutate(label = paste0(
  "italic(r)^2 == ", round(estimate^2, 2),
  " *','~ ", 
  ifelse(p.value < 0.001, "p < 0.001", paste0("p == ", round(p.value, 3)))
))


# Merge with max x/y position per shore to position text nicely
label_positions <- day_dat_all_shore %>%
 group_by(shore) %>%
  summarise(
    x = 15,
    y = 36
  ) %>%
  left_join(cor_stats, by = "shore")



GPP_ER_plots <- ggplot(day_dat_all_shore, aes(y = middle_ER_ab, x = middle_GPP, color = as.factor(shore), shape=shore)) +
  geom_point(size=2, alpha=0.35) +
      scale_y_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
    scale_x_continuous(trans = "log", breaks = scales::log_breaks(base = 10)) +
  xlab(expression(GPP~(mmol~O[2]~m^-3~d^-1))) +
  ylab(expression("|"~ER~"|"~(mmol~O[2]~m^-3~d^-1))) +
  geom_smooth(method="lm", se=F) +
  scale_color_manual(
    name = "Shore",
    values = c("BW" = "#3283a8", "GB" = "#a67d17", "SS" = "#136F63",  SH = "#c76640"),
        labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  scale_shape_manual(
    name = "Shore",
    values = c("BW" = 19, "GB" = 17, "SS" = 1, "SH" = 2),
       labels = c(BW = "West shore large inflow", GB = "East shore small inflow", 
                   SS = "West shore no inflow", SH = "East shore no inflow")) +
  theme_classic() +
    geom_text(data = label_positions, aes(x = x, y = y, label = label),
          parse = TRUE, inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3.5) +
      facet_grid(shore~.)


GPP_ER_plots

```


```{r, warning=F, echo=FALSE, include=T, fig.width=8, fig.height=8}

metab_grid <- ggarrange(
  GPP_ER_plots,
  GPP_light_plots,
  ER_temp_plots,
  align=c("v"),
  #label.x = 0.1,
  #label.y = 1,
  #hjust = 0.1,
  vjust = 1,
    common.legend = TRUE, 
  legend = "bottom",
 ncol = 3, nrow = 1)

metab_grid

```



```{r, warning=F, size = 'small', echo=F, include=F, fig.width=6, fig.height=4}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/Fig5_Met_cor_panel_long.png", plot = metab_grid, width = 7.5, height = 7, units = "in")

```



##### GB GPP - SH GPP v  GB light - SH light 




```{r, warning=F, echo=FALSE, include=F, fig.width=7, fig.height=5}
week_df_wide_shore <- rbind(
  df_BW_p,
  df_SS_p,
  df_GB_p,
  df_SH_p)

names(week_df_wide_shore)

library(dplyr)
library(tidyr)
library(purrr)
library(stringr)

# Get unique shores
unique_shores <- unique(week_df_wide_shore$shore)

# All possible shore pairs (excluding self-comparisons)
shore_pairs <- combn(unique_shores, 2, simplify = FALSE)

compute_pair_diff <- function(df, shore1, shore2) {
  df1 <- df %>%
    filter(shore == shore1) %>%
    select(week, WaterYear, middle_GPP) %>%
    rename(GPP1 = middle_GPP)
  
  df2 <- df %>%
    filter(shore == shore2) %>%
    select(week, WaterYear, middle_GPP) %>%
    rename(GPP2 = middle_GPP)
  
  full_join(df1, df2, by = c("week", "WaterYear")) %>%
    mutate(
      GPP_diff = GPP1 - GPP2,
      shore_pair = paste0(shore1, "_", shore2)
    )
}

# Use this instead if you want a tidy long format
tidy_diff_GPP <- map_dfr(shore_pairs, ~ compute_pair_diff(week_df_wide_shore, .x[1], .x[2]))



compute_pair_diff_ER <- function(df, shore1, shore2) {
  df1 <- df %>%
    filter(shore == shore1) %>%
    select(week, WaterYear, ER_abs) %>%
    rename(ER1 = ER_abs)
  
  df2 <- df %>%
    filter(shore == shore2) %>%
    select(week, WaterYear, ER_abs) %>%
    rename(ER2 = ER_abs)
  
  full_join(df1, df2, by = c("week", "WaterYear")) %>%
    mutate(
      ER_diff = ER1 - ER2,
      shore_pair = paste0(shore1, "_", shore2)
    )
}

# Use this instead if you want a tidy long format
tidy_diff_ER <- map_dfr(shore_pairs, ~ compute_pair_diff_ER(week_df_wide_shore, .x[1], .x[2]))




compute_pair_diff_light <- function(df, shore1, shore2) {
  df1 <- df %>%
    filter(shore == shore1) %>%
    select(week, WaterYear, light_mean) %>%
    rename(light1 = light_mean)
  
  df2 <- df %>%
    filter(shore == shore2) %>%
    select(week, WaterYear, light_mean) %>%
    rename(light2 = light_mean)
  
  full_join(df1, df2, by = c("week", "WaterYear")) %>%
    mutate(
      light_diff = light1 - light2,
      shore_pair = paste0(shore1, "_", shore2)
    )
}

# Use this instead if you want a tidy long format
tidy_diff_light <- map_dfr(shore_pairs, ~ compute_pair_diff_light(week_df_wide_shore, .x[1], .x[2]))




compute_pair_diff_temp <- function(df, shore1, shore2) {
  df1 <- df %>%
    filter(shore == shore1) %>%
    select(week, WaterYear, lake_tempC) %>%
    rename(temp1 = lake_tempC)
  
  df2 <- df %>%
    filter(shore == shore2) %>%
    select(week, WaterYear, lake_tempC) %>%
    rename(temp2 = lake_tempC)
  
  full_join(df1, df2, by = c("week", "WaterYear")) %>%
    mutate(
      temp_diff =temp1 - temp2,
      shore_pair = paste0(shore1, "_", shore2)
    )
}

# Use this instead if you want a tidy long format
tidy_diff_temp <- map_dfr(shore_pairs, ~ compute_pair_diff_temp(week_df_wide_shore, .x[1], .x[2]))


diff_df_shores <- tidy_diff_GPP %>%
  left_join(tidy_diff_ER%>%dplyr::select(week,WaterYear,ER_diff, shore_pair),
            by=c("week","WaterYear", "shore_pair")) %>%
  left_join(tidy_diff_light%>%dplyr::select(week,WaterYear,light_diff, shore_pair),
            by=c("week","WaterYear", "shore_pair")) %>%
    left_join(tidy_diff_temp%>%dplyr::select(week,WaterYear,temp_diff, shore_pair),
            by=c("week","WaterYear", "shore_pair")) %>%
      left_join(week_df_wide_shore%>%dplyr::select(week,WaterYear,lake_tempC, light_mean),
            by=c("week","WaterYear"))
```

### GPP differences by shore pairs and light 

```{r, warning=F, echo=FALSE, include=T, fig.width=7, fig.height=4.5}

light_plots <- ggplot(diff_df_shores, aes(y = GPP_diff, x = light_mean, color = as.factor(shore_pair), shape=shore_pair)) +
  geom_point(size=2, alpha=0.75) +
   scale_color_viridis_d(option = "viridis",  name = "Shore pair") +
  theme_classic()  +
   geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
      facet_wrap(~shore_pair)
light_plots

```


### GPP differences by shore pairs and  light differences by shore pairs


```{r, warning=F, echo=FALSE, include=T, fig.width=7, fig.height=4.5}
light_diff_plots <- ggplot(diff_df_shores, aes(y = GPP_diff, x = light_diff, color = as.factor(shore_pair), shape=shore_pair)) +
  geom_point(size=2, alpha=0.75) +
  theme_classic()  +
     scale_color_viridis_d(option = "viridis",  name = "Shore pair") +
     geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
     geom_vline(xintercept = 0, linetype = "dashed", color = "grey25") +
      facet_wrap(~shore_pair)
light_diff_plots
```


### ER differences by shore pairs and temp  


```{r, warning=F, echo=FALSE, include=T, fig.width=7, fig.height=4.5}
temp_plots <- ggplot(diff_df_shores, aes(y = ER_diff, x = lake_tempC, color = as.factor(shore_pair), shape=shore_pair)) +
  geom_point(size=2, alpha=0.75) +
  theme_classic()  +
     scale_color_viridis_d(option = "viridis",  name = "Shore pair") +
     geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
      facet_wrap(~shore_pair)
temp_plots
```


### ER differences by shore pairs and temp by shore pairs


```{r, warning=F, echo=FALSE, include=T, fig.width=7, fig.height=4.5}
temp_diff_plots <- ggplot(diff_df_shores, aes(y = ER_diff, x = temp_diff, color = as.factor(shore_pair), shape=shore_pair)) +
  geom_point(size=2, alpha=0.75) +
  theme_classic()  +
     scale_color_viridis_d(option = "viridis",  name = "Shore pair") +
     geom_hline(yintercept = 0, linetype = "dashed", color = "grey25") +
     geom_vline(xintercept = 0, linetype = "dashed", color = "grey25") +
      facet_wrap(~shore_pair)
temp_diff_plots
```










