---
title: 'Hydro-climate characteristics'
author: "Kelly Loria"
date: "`r Sys.Date()`"
output:
   html_document:
    theme: united
    highlight: tango
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style type="text/css">
body, td {font-size: 13px;}
code.r{font-size: 9px;}
pre {font-size: 11px}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F, message = F)
knitr::opts_knit$set(root.dir = '/Users/kellyloria/Documents/Publications/')
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

```


```{r, include=FALSE}
library(snotelr)
library(tidyverse)
library(lubridate)
library(readr)
library(ggpubr)
library(ggplot2)
library(ggdist)
library(dataRetrieval)
library(lme4)
library(lmerTest)
library(MuMIn)

site_colors <- c(
  "BWL" = "#3283a8",
  "SS" = "#136F63",
  "GBL" = "#a67d17",
  "SH" = "#c76640"
)


catch_colors <- c(
  "BW" = "#3283a8",
  "SS" = "#136F63",
  "GB" = "#a67d17",
  "SH" = "#c76640")


```

## Calculating hydrology characteristics for stream flow data

### 1. Flow Duration Analysis

Bring in stream flow to look at snow to flow dynamics from USGS stream gage network ([streamstats](https://streamstats.usgs.gov/ss/))

```{r eval=TRUE, echo = TRUE, error=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# identify and scrape data from USGS gages for target sites (BW and GB)

# Define the site numbers for "GB" and "BW"
siteNo_GB <- "10336730"
siteNo_BW <- "10336660"

# Define the parameter codes for flow and stage
pCode_flow <- "00060"
pCode_stage <- "00065"

# Set the start date to "1980-01-01" and end date to today (current date)
start.date <- "2003-09-30"
end.date <- "2024-10-30" #Sys.Date()  # Use the current date as the end date

# Ensure that dplyr functions are correctly used
flow_data_GB <- readNWISdata(siteNumbers = siteNo_GB, parameterCd = pCode_flow, startDate = start.date, endDate = end.date) %>%
  mutate(site = "GBL", catch = "GB") %>%
  dplyr::rename(date = dateTime, dischargeCFS = X_00060_00003) %>%
  mutate(
    dischargeCMS = dischargeCFS * 0.0283168,
    scale_Q = ((dischargeCFS * 0.0283168) / 10.64485)) %>%
    dplyr::select(date, dischargeCFS, site, catch, dischargeCMS, scale_Q)

# View the processed data
print(head(flow_data_GB))

flow_data_BW <- readNWISdata(siteNumbers = siteNo_BW, parameterCd = pCode_flow, startDate = start.date, endDate = end.date) %>%
  mutate(site = "BWL", catch = "BW") %>%
   dplyr::rename(date = dateTime, dischargeCFS = X_00060_00003) %>%
  mutate(
    dischargeCMS = dischargeCFS * 0.0283168,
    scale_Q = ((dischargeCFS * 0.0283168) / 29.00787)
  ) %>%
  dplyr::select(date, dischargeCFS, site, catch, dischargeCMS, scale_Q)


# Combine data for both sites
flow_data <- rbind(flow_data_GB, flow_data_BW)
```


## 2. Hydro-climate characterization

Major question to address:

-   How do the watersheds filter surface water inputs to streams based on differences in local climate (precipitation events, snow-accumulation and snow-melt)?

##### Function for water year:

```{r eval=TRUE, echo = T, error=FALSE, warning=FALSE, message=FALSE}
# fxn for water year
water_year <- function(data) {
  data %>%
    mutate(date = ymd(date)) %>%
    mutate(WaterYear = if_else(month(date) >= 10, year(date) + 1, year(date)))
}
```

##### Read in data from SNOTEL

```{r eval=TRUE, echo = F, error=FALSE, warning=FALSE, message=FALSE}
# read in the sites data for all SNOTEL sites
target_snow_data <- snotelr::snotel_download(network = "sntl",
                                             site_id = c(848, 615), 
                                             metric = TRUE, internal = TRUE)
target_snow_data$date<- as.Date(target_snow_data$date)

# transform for water year:
target_snow_dat<- water_year(target_snow_data)

#Trim for columns 
target_snow_df <- target_snow_dat %>%
  filter(WaterYear>2003) %>%
  filter(date < as.Date("2024-10-10")) %>%
  mutate(site = case_when(
    site_id == 615 ~ "GBL",
    site_id %in% c(848) ~ "BWL")) %>%
  dplyr::select(site_name,site_id,date,snow_water_equivalent,precipitation_cumulative,
         temperature_max,temperature_min,temperature_mean,precipitation,WaterYear,
         site)
```


## B. Melt and stream flow.

```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}
snowflow_dat <- left_join(target_snow_df, 
                          flow_data, by = c("date", "site")) %>%
  mutate(dischargeCMD = scale_Q * 86400) %>%
  group_by(site, WaterYear)%>%
  arrange(date) %>%  
  mutate(accum_SWE = cumsum(snow_water_equivalent),
         accum_Qm3D = cumsum(dischargeCMD))
  
``` 



### Estimate values for: 

- Total accumulated SWE per water year in mm/yr

- Water yield (cms/km yr)

- Max SWE measurement mm

- Max precipitation accumulation (ppt) in mm 


```{r, echo=T, error=FALSE, warning=FALSE, include=T, message=FALSE}

snowflow_dat_sum <- snowflow_dat%>%
  filter(WaterYear<2025) %>%
  group_by(site, WaterYear) %>%
 dplyr::summarise(Total_SWE = max(accum_SWE, na.rm=T),
            Water_yield = max(accum_Qm3D, na.rm = T),
            Max_SWE = max(snow_water_equivalent, na.rm=T),
            Total_ppt = max(precipitation_cumulative, na.rm=T),
            scale_pk_Q = max(scale_Q, na.rm = T)
            )


### get 20 year water year averages
snowflow_HA <- snowflow_dat_sum%>%
  filter(WaterYear<2025) %>%
  group_by(site) %>%
   dplyr::summarise(mean_SWE_acc = mean(Total_SWE, na.rm=T),
            mean_Water_yield = mean(Water_yield, na.rm = T),
            mean_SWE = mean(Max_SWE, na.rm = T),
            mean_ppt_acc = mean(Total_ppt, na.rm = T)
            )



snowflow_HA1 <- snowflow_dat_sum%>%
  filter(WaterYear>2020 & WaterYear<2024) %>%
  mutate(WY_lab = case_when(
    WaterYear %in% c(2021, 2022) ~ "dry",
    WaterYear %in% c(2023) ~ "wet",
    TRUE ~ NA_character_  )) %>%
    group_by(site,WY_lab) %>%
   dplyr::summarise(mean_SWE_acc = mean(Total_SWE, na.rm=T),
            mean_Water_yield = mean(Water_yield, na.rm = T),
            mean_SWE = mean(Max_SWE, na.rm = T),
            mean_ppt_acc = mean(Total_ppt, na.rm = T),
            m_pk_Q= mean(scale_pk_Q, na.rm=T)
            )

```


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}

ppt_accum_plots <- ggplot(snowflow_dat_sum, aes(x = WaterYear, y = Total_ppt*0.001, color = site, shape=site)) +
  annotate("rect", xmin = -Inf, xmax = 2021.5, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
annotate("rect", xmin = 2023.5, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "grey80", alpha = 0.3) +
  geom_point(size = 1.5, alpha = 0.95, position = position_dodge(width = 0.1)) +
  geom_line(position = position_dodge(width = 0.1))+
    geom_hline(yintercept = 1718.2429*0.001, col = "#3283a8", lty = 2) + 
  geom_hline(yintercept = 843.7667*0.001, col = "#a67d17", lty = 2) + 
  theme_bw() + 
 # geom_vline(xintercept = 2021.5, linetype = "dotted", color = "grey30") +
#    geom_vline(xintercept = 2023.5, linetype = "dotted", color = "grey30") +
  ylab(expression("PPT"~(m~y^-1))) +
  xlab(NULL) + scale_color_manual(values = site_colors) +
  theme(legend.position =  "none") +
        scale_shape_manual(name = "Shore",
                     values = c("BWL" = 19, 
                                "GBL" = 17)) +
        scale_x_continuous(breaks = seq(floor(min(snowflow_dat_sum$WaterYear)), ceiling(max(snowflow_dat_sum$WaterYear)), by = 5), labels = function(x) as.character(round(x)))
  
  
  
```


### streamflow for each catchment WY 22 and WY 23 


```{r, echo=FALSE, error=FALSE, warning=FALSE, include=F, message=FALSE}

snowflow_dat <- as.data.frame(snowflow_dat)

snowflow_dat$date <- as.Date(snowflow_dat$date)



flow_plot1 <- ggplot(
  snowflow_dat %>% filter(date > as.Date("2021-09-30") & date < as.Date("2023-09-14")),
  aes(x = date, y = scale_Q, color = site)
) +
  geom_line(position = position_dodge(width = 0.1)) +
  geom_vline(xintercept = as.Date("2022-09-30"), linetype = "dashed", color = "grey50",ltwd=0.5) +
  theme_classic() + 
  scale_x_date(
  date_breaks = "8 week",
  date_labels = "%b-%y",
  limits = c(as.Date("2021-09-29"), as.Date("2023-10-01"))) +
  ylab(expression("Streamflow"~(m^3~s^-1~km^2))) +
  xlab(NULL) + 
   annotate("text", x = as.Date("2022-08-20"), y = 0.03, label = "WY 2022", size = 4, fontface = "bold", color="grey50")  +
     annotate("text", x = as.Date("2022-11-10"), y = 0.03, label = "WY 2023", size = 4, fontface = "bold", color="grey50")+

  scale_color_manual(values = site_colors) +
  theme(legend.position = "none")


str(snowflow_dat)
```


### 20 years of SWE accumulation and water yield  

The dashed lines represent the site 20-year average annual (WY) values for total SWE or water catchment normalized water yield 

```{r, warning=F, echo=F,include=T, fig.width=8, fig.height=10}
library(cowplot)

# Create the main plot and the inset
main_plot <- flow_plot1
inset_plot <- ppt_accum_plots

# Combine using draw_plot() with positioning
combined_plot <- ggdraw() +
  draw_plot(main_plot) +  # full-size base plot
  draw_plot(inset_plot, 
            x = 0.07,     # horizontal position (0 = left, 1 = right)
            y = 0.59,     # vertical position (0 = bottom, 1 = top)
            width = 0.45,  # width of the inset (relative to full plot)
            height = 0.4) # height of the inset

# Show it
combined_plot


## align = hv in cow plot high light the years that mountain so that the y axis starts in the same way 
## scale_y_continours

### to scale the water yeild - scale_y_continuous(trans = "log")
```


```{r, warning=F, size = 'small', echo=F, include=F, fig.width=6, fig.height=4}
# ggsave("/Users/kellyloria/Documents/Publications/CH1\ biogeochem\ linkages/Figs/Hydro_panel_long.png", plot = combined_plot, width = 8.5, height = 4, units = "in")

```

